---
title: "Fitness Analyses"
output: html_notebook
---


```{r}
library(tidyverse)
library(ggplot2)
#library(lme4)
library(lmerTest)
```

# FIELD DATA

```{r}
area <- read.csv("~/Desktop/GitHub/TBDCFit/Data/FieldLeafArea.csv", header = TRUE)
germ <- read.csv("~/Desktop/GitHub/TBDCFit/Data/GermCollated.csv", header = TRUE)
key <- read.csv("~/Desktop/GitHub/TBDCFit/Data/pidTrtKey.csv", header = TRUE)
pods <- read.csv("~/Desktop/GitHub/TBDCFit/Data/ExitData.csv", header = TRUE)
TBseed <- read.csv("~/Desktop/GitHub/TBDCFit/Data/TBSeedCorrect.csv", header = TRUE)
DCseed <- read.csv("~/Desktop/GitHub/TBDCFit/Data/DCSeed.csv", header = TRUE)
```

## 1. Get seed set per plant

Remove unneeded rows from  pods

```{r}
pods <- pods %>%
  select(PID, num.pod.m)
```

Exclude any pods that matured later/had no mature pods

```{r}
pods <- pods[pods$num.pod.m != 0, ]
```



Make a binary column for holes in TB pods

```{r}
TBseed$binary <- 0
```

```{r}
for(i in 1:length(TBseed$PID)){
  if(TBseed[i, 3] > 0){
    TBseed[i, 5] <- 1
  } else if(TBseed[i, 3] <= 0){
    TBseed[i, 5] <- 0
  }
}

```

Seed mass per TB pod 

```{r}
TBseed$mass.per.pod <- TBseed$Mass..g. / TBseed$Total.Pods
```

Remove unnecessary columns fromm TBseed

```{r}
TBseed <- TBseed %>%
  select(PID, binary, mass.per.pod)
```


### Write a for loop to get avg seed number per pod for DC

```{r}
#1. List of unique PIDs in DCseed

DCpid <- unique(DCseed$pid)

#2. Make output dataset

DCseedout <- data.frame(pid = DCpid, 
                        pod.avg = 0)

#3. write the for loop 

for(i in 1:length(DCpid)){
  subset <- DCseed[DCseed$pid == DCpid[i], ]
  DCseedout[i, 2] <- mean(subset$num.m.seeds)
}
```


## 2. Get standardized seed set metric

1. Multiply avg seed set per plant by number of mature pods produced
2. Get median of control group seed set by each plant type
3. Divide each individual by that mean 
4. Combine into one dataset 

### Step 1


```{r}
DCseedout <- merge(DCseedout, pods, by.x = "pid", by.y = "PID")
TBseed <- merge(TBseed, pods, by.x = "PID", by.y = "PID")

DCseedout$tot.seed.set <- DCseedout$pod.avg * DCseedout$num.pod.m
TBseed$tot.seed.set <- TBseed$mass.per.pod * TBseed$num.pod.m
```


### Step 2

Select correct columns from key

```{r}
key <- key %>%
  select(pid, type, treatment, column)
```


```{r}
DCseedout <- merge(DCseedout, key, by = "pid")

DCseedout <- DCseedout %>%
  select(pid, type, treatment, column, tot.seed.set)

DCseedCON <- DCseedout[DCseedout$treatment == "CON", ]

medianDC <- median(DCseedCON$tot.seed.set)

```


```{r}
TBseed <- merge(TBseed, key, by.x = "PID", by.y = "pid")

TBseed <- TBseed %>%
  select(PID, type, treatment, column, binary, tot.seed.set)

TBseedCON <- TBseed[TBseed$treatment == "CON", ]

medianTB <- median(TBseedCON$tot.seed.set)

```


```{r}
DCseedout$stand.seed <- DCseedout$tot.seed.set / medianDC

TBseed$stand.seed <- TBseed$tot.seed.set / medianTB
```

## 3. Combine everything together

```{r}
germ <- germ %>%
  select(pid, prop.sprouted)

comb <- merge(area, germ, by.x = "PID", by.y = "pid")
#comb <- merge(comb, pods, by = "PID")

comb <- merge(comb, DCseedout, by.x = c("PID", "treatment", "type"), by.y = c("pid", "treatment", "type"), all.x = TRUE)
comb <- merge(comb, TBseed, by = c("PID", "treatment", "type"), all.x = TRUE)

comb$column <- paste(comb$column.x, comb$column.y, sep = "")
comb$column <- gsub("NA", "", comb$column)


comb$stand.seed.set <- paste(comb$stand.seed.x, comb$stand.seed.y, sep = "")
comb$stand.seed.set <- gsub("NA", "", comb$stand.seed.set)
```

Remove plants where we germinated seeds from immature pods

```{r}
comb <- comb[comb$stand.seed.set > 0, ]
```

Remove plants that didn't germinate at all **ASK BECKY**

```{r}
comb2 <- comb[comb$prop.sprouted > 0, ]
```


### Calculate fitness: 

```{r}
comb2$stand.seed.set <- as.numeric(comb2$stand.seed.set)
comb2$ln.stand.seed.set <- log(comb2$stand.seed.set)

comb2$rel.fitness <- comb2$prop.sprouted * comb2$ln.stand.seed.set
```

## 4. Graph! 

```{r}
fieldfitnessplot <- ggplot(data = comb2, aes(x = tot.area, y = rel.fitness)) + 
  geom_smooth(aes(linetype = type), color = "black", method = "lm", alpha = 0.2) + 
  scale_linetype_manual(values = c("solid", "dotdash")) + 
  geom_point(aes(shape = type,  color = treatment)) + 
  theme_bw() + 
  scale_color_manual(values = c("#1E88E5", "lime green", "orange", "#D81B60")) + 
  scale_shape_manual(values = c(16, 5)) + 
  labs(x = expression(paste("Leaf area consumed ", (cm^{2}))), y = "Relative fitness", color = "Treatment group",
       shape = "Hostplant", linetype = "Hostplant")

fieldfitnessplot

```




```{r}
ggsave("~/Desktop/GitHub/TBDCFit/Figures/fieldfitnessherb.png", fieldfitnessplot, width = 8, height = 5)
```


Look at subcomponents

Standardized seed set:


```{r}
fieldseedsetplot <- ggplot(data = comb2, aes(x = tot.area, y = ln.stand.seed.set)) + 
  geom_smooth(aes(linetype = type), color = "black", method = "lm", alpha = 0.2) + 
  scale_linetype_manual(values = c("solid", "dotdash")) + 
  geom_point(aes(shape = type,  color = treatment)) + 
  theme_bw() + 
  scale_color_manual(values = c("#1E88E5", "lime green", "orange", "#D81B60")) + 
  scale_shape_manual(values = c(16, 5)) + 
  labs(x = expression(paste("Leaf area consumed ", (cm^{2}))), y = "Standardized seed set", color = "Treatment group",
       shape = "Hostplant", linetype = "Hostplant")

fieldseedsetplot


```

Germination: 

```{r}
fieldgermplot <- ggplot(data = comb2, aes(x = tot.area, y = prop.sprouted)) + 
  geom_smooth(aes(linetype = type), color = "black", method = "lm", alpha = 0.2) + 
  scale_linetype_manual(values = c("solid", "dotdash")) + 
  geom_point(aes(shape = type,  color = treatment)) + 
  theme_bw() + 
  scale_color_manual(values = c("#1E88E5", "lime green", "orange", "#D81B60")) + 
  scale_shape_manual(values = c(16, 5)) + 
  labs(x = expression(paste("Leaf area consumed ", (cm^{2}))), y = "Germination success", color = "Treatment group",
       shape = "Hostplant", linetype = "Hostplant")

fieldgermplot

```



## 5. Stats! 

```{r}
fieldfitmod <- lmer(rel.fitness ~ tot.area*type + (1|column), data = comb2)

summary(fieldfitmod)
```

