---
title: "Floral Count Analysis"
output: html_notebook
---

This script will calculate the total number of flowers pollinated on each plant for the entirety of both the field and greenhouse studies. 

Roadmap: 

0. Load in the data
1. Select relevant columns and create output file
2. Write a for loop to add floral number by PID
3. Create an output csv

# 0. Load in the data 

```{r}
library(tidyverse)
library(ggplot2)
library(Rmisc)
```


```{r}
pollfield <- read.csv("~/Desktop/GitHub/TBDCFit/Data/pollination.csv", header = TRUE)
keyfield <- read.csv("~/Desktop/GitHub/TBDCFit/Data/pidTrtKey.csv", header = TRUE)
exitfield <- read.csv("~/Desktop/GitHub/TBDCFit/Data/ExitData.csv", header = TRUE)
```

# 1. Select relevant columns 

```{r}
pollfield <- pollfield %>%
  select(date, pid = PID, num.flowers)

pollfield <- pollfield[is.na(pollfield$num.flowers) == FALSE, ]

keyfield <- keyfield %>%
  select(pid, type, treatment)

exitfield <- exitfield %>%
  select(pid = PID, num.flower.unpol)

exitfield[exitfield$pid == 30, 2] <- 0
  
```

## Create an output file

```{r}
outputfield <- data.frame(
  pid = unique(keyfield$pid),
  tot.flowers = 0
)

outputfield <- outputfield %>%
  arrange(pid)
```

# 2. Write the for loop 

1. Subset pollination data by PID
2. Take the sum of the num.flowers column
3. Stick that sum in the output file

```{r}
flowernum <- function(dataframe, output){
  
  for(i in 1:length(output$pid)){
    k <- output[i, 1]
    subset <- dataframe[dataframe$pid == k, ]
    output[i, 2] <- sum(subset$num.flowers)
  }
   return(output)
}
```

## Run the function

```{r}
outputfield <- flowernum(dataframe = pollfield, output = outputfield)
```

## Merge with ending exit data - number of unpollinated flowers

```{r}
outputfield <- merge(outputfield, exitfield, by = "pid")

outputfield$tot.flowers <- outputfield$tot.flowers + outputfield$num.flower.unpol

outputfield <- outputfield %>%
  select(pid, tot.flowers)
```



# 3. Write to CSV 


```{r}
write.csv(x = outputfield, file = "~/Desktop/GitHub/TBDCFit/Data/FieldNumFlowers.csv", row.names = FALSE)
```

