---
title: "Germination analyses"
output: html_notebook
---

## 0. Load libraries and data

```{r}
library(tidyverse)
library(ggplot2)
library(lme4)
```

```{r}
herb <- read.csv("~/Desktop/GitHub/TBDCFit/Data/HerbivoryCleaned.csv", header = TRUE)
germ <- read.csv("~/Desktop/GitHub/TBDCFit/Data/GermCollated.csv", header = TRUE)
key <- read.csv("~/Desktop/GitHub/TBDCFit/Data/pidTrtKey.csv", header = TRUE)
```

## 1. Clean the data

Keep necessary columns

```{r}
herb <- herb %>%
  select(pid, type, treatment, num.leaf)

germ <- germ %>%
  select(pid, flat, num.seeds, prop.sprouted)

key <- key %>%
  select(pid, column)
```

Combine datasets

```{r}
comb <- merge(herb, germ, by = "pid")
comb <- merge(comb, key, by = "pid")
```

Convert num leaf to area

```{r}
combDC <- comb[comb$type == "DC", ]
combTB <- comb[comb$type == "TB", ]

combDC$area.leaf <- combDC$num.leaf * (((104.55 + 105.84 + 91.82)/3))
combTB$area.leaf <- combTB$num.leaf * (1.5*((143.17 + 212.06 + 152.22)/3))

comb <- rbind(combDC, combTB)
comb$area.leaf <- comb$area.leaf / 10000

comb$ln.area.leaf <- log(comb$area.leaf + 1)
 

```



## 2. Run analyses 

## FOR POSTER

germ success by herbivory (DC and TB together)
```{r}
herbgerm <-  glmer(prop.sprouted ~ area.leaf*type + (1|flat), data = comb, family = binomial, weights = num.seeds)

summary(herbgerm)
anova(herbgerm, test = "Chisq")
```



### Graph

```{r}
herbgermplot <- ggplot(data = comb, aes(x = area.leaf, y = prop.sprouted, color = type)) + 
  theme_bw() + 
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE) + 
  labs(x = "Leaf surface area consumed (m^2)", y = "Proportion of seeds germinated", color = "Plant type")

herbgermplot
```






## OTHER ANALYSES
Column by germination success

```{r}
colgerm <- glmer(prop.sprouted ~ column + (1|flat), data = comb, family = binomial, weights = num.seeds)

summary(colgerm)
anova(colgerm, test = "Chisq")
```

Germination success by treatment

```{r}
treatgerm <- glmer(prop.sprouted ~ treatment + (1|flat), data = comb, family = binomial, weights = num.seeds)

summary(treatgerm)
anova(treatgerm, test = "Chisq")
```

DC only:
```{r}
treatgermDC <- glmer(prop.sprouted ~ treatment + (1|flat), data = comb[comb$type == "DC", ], family = binomial, weights = num.seeds)

summary(treatgermDC)
anova(treatgermDC, test = "Chisq")
```


TB only:
```{r}
treatgermTB <- glmer(prop.sprouted ~ treatment + (1|flat), data = comb[comb$type == "TB", ], family = binomial, weights = num.seeds)

summary(treatgermTB)
anova(treatgermTB, test = "Chisq")
```


Herbivory vs. germination success

DC:

```{r}
herbDCgerm <-  glmer(prop.sprouted ~ num.leaf + (1|flat), data = comb[comb$type == "DC", ], family = binomial, weights = num.seeds)

summary(herbDCgerm)
```

TB: 

```{r}
herbTBgerm <-  glmer(prop.sprouted ~ num.leaf + (1|flat), data = comb[comb$type == "TB", ], family = binomial, weights = num.seeds)

summary(herbTBgerm)
```



## Try doing it without moldy DC seeds 

```{r}
comb2 <- comb[comb$num.seeds >= 10, ]
```

Germination success by treatment

```{r}
treatgerm2 <- glmer(prop.sprouted ~ treatment + (1|flat), data = comb2, family = binomial, weights = num.seeds)

summary(treatgerm2)
#anova(treatgerm, test = "Chisq")
```

```{r}
treattypegerm <- glmer(prop.sprouted ~ treatment + type + (1|flat), data = comb2, family = binomial, weights = num.seeds)

summary(treattypegerm)
```

Don't want this one (interaction not significant)
```{r}
treattypegerm2 <- glmer(prop.sprouted ~ treatment*type + (1|flat), data = comb2, family = binomial, weights = num.seeds)

summary(treattypegerm2)
anova(treattypegerm2)
```


Herbivory by germ 

```{r}
herbgermDC2 <-  glmer(prop.sprouted ~ num.leaf + (1|flat), data = comb2[comb2$type == "DC", ], family = binomial, weights = num.seeds)

summary(herbgermDC2)
```

```{r}
ggplot(aes(x = num.leaf, y = prop.sprouted, color = treatment), data = comb2[comb2$type == "DC", ]) + 
  theme_bw() + 
  geom_point() + 
 # geom_smooth(method = "lm") + 
  scale_color_manual(values = c("#1E88E5", "lime green", "orange", "#D81B60")) + 
  labs(x = "Number of leaves consumed", y = "Proportion of seeds sprouted", title = "A) Devil's claw")
```



```{r}
herbgermTB2 <-  glmer(prop.sprouted ~ num.leaf + (1|flat), data = comb2[comb2$type == "TB", ], family = binomial, weights = num.seeds)

summary(herbgermTB2)
```

```{r}
ggplot(aes(x = num.leaf, y = prop.sprouted, color = treatment), data = comb2[comb2$type == "TB", ]) + 
  theme_bw() + 
  geom_point() + 
  #geom_smooth(method = "lm") + 
  scale_color_manual(values = c("#1E88E5", "lime green", "orange", "#D81B60")) + 
  labs(x = "Number of leaves consumed", y = "Proportion of seeds sprouted", title = "B) Tobacco")
```




