---
title: "Graphs and Analyses for Evolution"
output: html_notebook
---

This script makes graphs for my 2022 Evolution talk. 

Plan of attack: 

1) Make 3-level "theoretical" figure about expectations for herbivory
2) Make Histograms of herbivory by treatment group from the 2020 leaf scanner experiment 
3) Remake 2021 seed set graph to include all seed set plants (still excluding zeros)
4) Rerun stats on all seed set plants (excluding zeros still)
5) Run new stats on binary: did the plants produce seed? (By herbivory and plant type)


# 0. Load in packages

```{r}
library(dplyr)
library(ggplot2)
library(lmerTest)
```

# 1. Make theoretical figure with nice distributions to match results figure 

## Game plan: 

A. Come up with reasonable centers for each distribution
B. Make dataset with treatment, plant type, and different normal distributions for herbivory and seed set for the controls (centered on zero). 
C. Repeat for WAND, WE, WOWE
D. Graph it in increments to step through each treatment separately 


## A. Centers for distributions

CON (same for DC and TB): 
Herb: 0, SD 0 
Seed set: 0, SD 0.25

WAND
TB Herb: .25, SD .025
TB seed set: -1, SD .25
DC Herb: .25, SD .025
DC seed set: -1.25, SD .25

WE
TB Herb: .1, SD .025
TB seed set: -.5, SD .25
DC Herb: .1, SD .025
DC seed set: -.6, SD .25

WOWE
TB Herb: .5, SD .025
TB Seed set: -2, SD .25
DC Herb: .5, SD .025
DC Seed set: -2.5, SD .25


```{r}
set.seed(5)
```



## B. Make dataset for Controls

Some standardization: 10 datapoints per treatment group (for a total of 80)

```{r}
CONTB <- data.frame(
  pid = 1:10,
  treatment = "CON", 
  type = "TB", 
  herb = rnorm(10, mean = 0, sd = 0), 
  seedset = rnorm(10, mean = 0, sd = .25)
)
```

```{r}
CONDC <- data.frame(
  pid = 11:20,
  treatment = "CON", 
  type = "DC", 
  herb = rnorm(10, mean = 0, sd = 0), 
  seedset = rnorm(10, mean = 0, sd = .25)
)
```

```{r}
theodata <- rbind(CONTB, CONDC)
```


## C. Make for other three treatment groups


```{r}
WANDTB <- data.frame(
  pid = 21:30,
  treatment = "WAND", 
  type = "TB", 
  herb = rnorm(10, mean = 0.25, sd = 0.025), 
  seedset = rnorm(10, mean = -1, sd = .25)
)
```


```{r}
theodata <- rbind(theodata, WANDTB)
```


```{r}
WANDDC <- data.frame(
  pid = 31:40,
  treatment = "WAND", 
  type = "DC", 
  herb = rnorm(10, mean = 0.25, sd = 0.025), 
  seedset = rnorm(10, mean = -1.25, sd = .25)
)
```

```{r}
theodata <- rbind(theodata, WANDDC)
```



```{r}
WETB <- data.frame(
  pid = 41:50,
  treatment = "WE", 
  type = "TB", 
  herb = rnorm(10, mean = 0.1, sd = 0.025), 
  seedset = rnorm(10, mean = -.5, sd = .25)
)
```

```{r}
theodata <- rbind(theodata, WETB)
```

```{r}
WEDC <- data.frame(
  pid = 51:60,
  treatment = "WE", 
  type = "DC", 
  herb = rnorm(10, mean = 0.1, sd = 0.025), 
  seedset = rnorm(10, mean = -.6, sd = .25)
)
```

```{r}
theodata <- rbind(theodata, WEDC)
```



```{r}
WOWETB <- data.frame(
  pid = 61:70,
  treatment = "WOWE", 
  type = "TB", 
  herb = rnorm(10, mean = 0.5, sd = 0.025), 
  seedset = rnorm(10, mean = -2, sd = .25)
)
```

```{r}
theodata <- rbind(theodata, WOWETB)
```

```{r}
WOWEDC <- data.frame(
  pid = 71:80,
  treatment = "WOWE", 
  type = "DC", 
  herb = rnorm(10, mean = 0.5, sd = 0.025), 
  seedset = rnorm(10, mean = -2.5, sd = .25)
)
```

```{r}
theodata <- rbind(theodata, WOWEDC)
```

## D. Make incremental graphs

Total graph just to check: 

```{r}
totalplot <- ggplot(data = theodata, aes(x = herb, y = seedset, shape = type)) + 
  geom_smooth(aes(linetype = type), color = "black", method = "lm", alpha = 0.2) + 
  scale_linetype_manual(values = c("solid", "dotdash")) + 
  geom_point(aes(color = treatment)) + 
  theme_bw() + 
  ylim(-3.1, 0.6) + 
  xlim(0, .55) + 
  scale_color_manual(values = c("#1E88E5", "lime green", "orange", "#D81B60")) + 
  scale_shape_manual(values = c(16, 5)) + 
  labs(x = expression(paste("Leaf area consumed ", (m^{2}))), y = "Relative Fitness", 
       color = "Treatment group", shape = "Hostplant", linetype = "Hostplant") 

totalplot

ggsave("~/Desktop/GitHub/TBDCFit/Figures/EvolutionGraphs/totaltheo.png", totalplot, width = 8, height = 5)

```

We like it! Now on to each separate plot

WAND

```{r}
WANDplot <- ggplot(data = theodata[theodata$treatment == "CON" | theodata$treatment == "WAND", ], 
                   aes(x = herb, y = seedset, shape = type)) + 
  geom_point(aes(color = treatment)) + 
  theme_bw() + 
  ylim(-3.1, 0.6) + 
  xlim(0, .55) + 
  scale_color_manual(values = c("#1E88E5", "lime green")) + 
  scale_shape_manual(values = c(16, 5)) + 
  labs(x = expression(paste("Leaf area consumed ", (m^{2}))), y = "Relative Fitness", 
       color = "Treatment group", shape = "Hostplant") 

WANDplot

ggsave("~/Desktop/GitHub/TBDCFit/Figures/EvolutionGraphs/WANDtheo.png", WANDplot, width = 8, height = 5)

```

WE

```{r}
WEplot <- ggplot(data = theodata[theodata$treatment != "WOWE", ], aes(x = herb, y = seedset, shape = type)) + 
  geom_point(aes(color = treatment)) + 
  theme_bw() + 
  ylim(-3.1, 0.6) + 
  xlim(0, .55) + 
  scale_color_manual(values = c("#1E88E5", "lime green", "orange")) + 
  scale_shape_manual(values = c(16, 5)) + 
  labs(x = expression(paste("Leaf area consumed ", (m^{2}))), y = "Relative Fitness", 
       color = "Treatment group", shape = "Hostplant") 

WEplot

ggsave("~/Desktop/GitHub/TBDCFit/Figures/EvolutionGraphs/WEtheo.png", WEplot, width = 8, height = 5)

```

WOWE

```{r}
WOWEplot <- ggplot(data = theodata, aes(x = herb, y = seedset, shape = type)) + 
  geom_point(aes(color = treatment)) + 
  theme_bw() + 
  ylim(-3.1, 0.6) + 
  xlim(0, .55) + 
  scale_color_manual(values = c("#1E88E5", "lime green", "orange", "#D81B60")) + 
  scale_shape_manual(values = c(16, 5)) + 
  labs(x = expression(paste("Leaf area consumed ", (m^{2}))), y = "Relative Fitness", 
       color = "Treatment group", shape = "Hostplant") 

WOWEplot

ggsave("~/Desktop/GitHub/TBDCFit/Figures/EvolutionGraphs/WOWEtheo.png", WOWEplot, width = 8, height = 5)

```

# 2. Make histograms from leaf scanner expt. 

Game plan: 

A. Load in leaf scanner data
B. Calculate total herbivory using for loops 
C. Separate into columns I need (ID, treatment, type, total herbivory)
D. Make histograms with different fills by type in the same color for each treatment 


## A. Load in leaf scanner data and clean

```{r}
data <- read.csv("~/Desktop/MsCcHSFeedJan1MOD.csv")
scan <- read.csv("~/Desktop/MsCcHSFeedLeafScanFinal.csv", header = T)
```

```{r}
data <- data[data$fate != "dead" & data$fate != "quink" & data$fate != "wander*" & data$fate != "?", ]
data <- data[complete.cases(data[, 1]), ]
data$fate <- factor(data$fate, levels = c("wander", "em", "wowe", "wowe mongo"))

```


## B. Run the for loop


```{r}
#1
scan$comb <- paste(scan$Caterpillar.ID, "_", scan$Leaf.ID)

#0
unique <- unique(scan$comb)
consumed <- as.data.frame(unique)
consumed$area <- 0

#2-4
for (i in 1:length(consumed$unique)){
    subset <- filter(scan, scan$comb == consumed[i, 1])
    value <- max(subset$Leaf.Area) - min(subset$Leaf.Area)
    consumed[i, 2] <- value
}  

#5
consumed <- consumed %>%
  separate(unique, c("catID", "leafID"), "_")

#6
ID <- unique(consumed$catID)
consumedsum <- as.data.frame(ID)
consumedsum$totalarea <- 0

#7
for (i in 1:length(consumedsum$ID)){
  subset2 <- filter(consumed, consumed$catID == consumedsum[i, 1])
  value2 <- sum(subset2$area)
  consumedsum[i, 2] <- value2
}

#8
consumedsum$ID <- as.numeric(consumedsum$ID)

consumedsum <- consumedsum[consumedsum$ID %in% data$ID, ]

data <- data[data$ID %in% consumedsum$ID, ]

consumedsum <- consumedsum[order(consumedsum$ID), ]

data$area <- consumedsum$totalarea

data$area <- data$area / 10000

```


## C. Pare down into columns I need

```{r}
scandata <- data %>%
  select(ID, food, fate, area)
```

## D. Make histogram

WAND

```{r}
WANDhist <- ggplot(data = scandata[scandata$fate == "wander", ], aes(x = area)) + 
  geom_density(aes(fill = food), color = "lime green", position = "identity", alpha = 0.5) + 
  theme_bw() + 
  xlim(0, .6) + 
  scale_fill_manual(values = c("white", "lime green")) + 
  labs(x = expression(paste("Leaf area consumed ", (m^{2}))), y = "Frequency", fill = "Hostplant")

WANDhist

ggsave("~/Desktop/GitHub/TBDCFit/Figures/EvolutionGraphs/WANDhist.png", WANDhist, width = 8, height = 2)
```

WE

```{r}
WEhist <- ggplot(data = scandata[scandata$fate == "em", ], aes(x = area)) + 
  geom_density(aes(fill = food), color = "orange", position = "identity", alpha = 0.5) + 
  theme_bw() + 
  xlim(0, .6) + 
  scale_fill_manual(values = c("white", "orange")) + 
  labs(x = expression(paste("Leaf area consumed ", (m^{2}))), y = "Frequency", fill = "Hostplant")

WEhist

ggsave("~/Desktop/GitHub/TBDCFit/Figures/EvolutionGraphs/WEhist.png", WEhist, width = 8, height = 2)
```

WOWE

```{r}
WOWEhist <- ggplot(data = scandata[scandata$fate == "wowe mongo", ], aes(x = area)) + 
  geom_density(aes(fill = food), color = "#D81B60", position = "identity", alpha = 0.5) + 
  theme_bw() + 
  xlim(0, .6) + 
  scale_fill_manual(values = c("white", "#D81B60")) + 
  labs(x = expression(paste("Leaf area consumed ", (m^{2}))), y = "Frequency", fill = "Hostplant")

WOWEhist

ggsave("~/Desktop/GitHub/TBDCFit/Figures/EvolutionGraphs/WOWEhist.png", WOWEhist, width = 8, height = 2)
```


# 3. Remake seed set graph to include all seed sets (excluding zeros)

Gameplan: 

A. Load in datasets and rerun code 
B. Redo data analysis to include all plants with a seed set metric
C. Remake graph according to the new dataset

## A. Load in dataset

```{r}
herb <- read.csv("~/Desktop/GitHub/TBDCFit/Data/HerbivoryCleaned.csv", header = TRUE)
key <- read.csv("~/Desktop/GitHub/TBDCFit/Data/pidTrtKey.csv", header = TRUE)
pods <- read.csv("~/Desktop/GitHub/TBDCFit/Data/ExitData.csv", header = TRUE)
TBseed <- read.csv("~/Desktop/GitHub/TBDCFit/Data/TBSeed.csv", header = TRUE)
DCseed <- read.csv("~/Desktop/GitHub/TBDCFit/Data/DCSeed.csv", header = TRUE)
```

### Get seed set per plant


Remove the individuals that had mature pods that we couldn't measure due to damage/mold

```{r}
TBseed <- TBseed[TBseed$pid != 23, ]
TBseed <- TBseed[TBseed$pid != 141, ]

pods <- pods[pods$PID != 23, ]
pods <- pods[pods$PID != 141, ]
```

Remove unneeded rows from TBseed and pods

```{r}
TBseed <- TBseed %>%
  select(pid, mature, kept, pod.avg, holes.)

pods <- pods %>%
  select(PID, num.pod.m)
```

### Write a for loop to get avg seed number per pod for DC

```{r}
#1. List of unique PIDs in DCseed

DCpid <- unique(DCseed$pid)

#2. Make output dataset

DCseedout <- data.frame(pid = DCpid, 
                        pod.avg = 0)

#3. write the for loop 

for(i in 1:length(DCpid)){
  subset <- DCseed[DCseed$pid == DCpid[i], ]
  DCseedout[i, 2] <- mean(subset$num.m.seeds)
}
```

### Remove DC where we couldn't find pods / pods rotten

```{r}
DCseedout <- DCseedout[DCseedout$pid != 78, ]
DCseedout <- DCseedout[DCseedout$pid != 140, ]
```

### Remove pods with spodoptera damage

```{r}
TBseed <- TBseed[TBseed$holes. != "yes", ]
```

### Remove TB plants without mature seeds

```{r}
TBseed <- TBseed[complete.cases(TBseed[, 4]), ]
```

### Convert TB pod masses to seed masses

```{r}
TBseed$seed.avg <- TBseed$pod.avg - 82.9 ##average mass of seed pod husk from 5/30
TBseed <- TBseed[TBseed$seed.avg > 0,  ]

TBseed <- TBseed %>%
  select(pid, seed.avg)
```


###  Get standardized seed set metric

1. Multiply avg seed set per plant by number of mature pods produced
2. Get mean of control group seed set by each  plant type
3. Divide each individual by that mean 
4. Combine into one dataset 

#### Step 1


```{r}
DCseedout <- merge(DCseedout, pods, by.x = "pid", by.y = "PID")
TBseed <- merge(TBseed, pods, by.x = "pid", by.y = "PID")

DCseedout$tot.seed.set <- DCseedout$pod.avg * DCseedout$num.pod.m
TBseed$tot.seed.set <- TBseed$seed.avg * TBseed$num.pod.m
```


```{r}
DCseedout <- merge(DCseedout, key, by = "pid")

DCseedout <- DCseedout %>%
  select(pid, treatment, tot.seed.set)

DCseedCON <- DCseedout[DCseedout$treatment == "CON", ]

medianDC <- median(DCseedCON$tot.seed.set)

```


```{r}
TBseed <- merge(TBseed, key, by = "pid")

TBseed <- TBseed %>%
  select(pid, treatment, tot.seed.set)

TBseedCON <- TBseed[TBseed$treatment == "CON", ]

medianTB <- median(TBseedCON$tot.seed.set)

```


#### Step 2

```{r}
DCseedout$stand.seed <- DCseedout$tot.seed.set / medianDC

TBseed$stand.seed <- TBseed$tot.seed.set / medianTB
```

### Merge herbivory and key dataset

```{r}
herb <- herb %>%
  select(pid, type, num.leaf)

key <- key %>%
  select(pid, treatment, column)

comb <- merge(herb, key, by = "pid")
```

### Get leaf number to area

```{r}
combDC <- comb[comb$type == "DC", ]
combTB <- comb[comb$type == "TB", ]

combDC$area.leaf <- combDC$num.leaf * (((104.55 + 105.84 + 91.82)/3))
combTB$area.leaf <- combTB$num.leaf * (1.5*((143.17 + 212.06 + 152.22)/3))

comb <- rbind(combDC, combTB)
comb$area.leaf <- comb$area.leaf / 10000

#comb$ln.area.leaf <- log(comb$area.leaf + 1)
 

```

## B.  Merge with standardized seed set for all with seed set metric

```{r}
comb <- merge(comb, DCseedout, by = c("pid", "treatment"), all.x = TRUE)
comb <- merge(comb, TBseed, by = c("pid", "treatment"), all.x = TRUE)

comb$stand.seed.set <- paste(comb$stand.seed.x, comb$stand.seed.y, sep = "")
comb$stand.seed.set <- gsub("NA", "", comb$stand.seed.set)

comb$stand.seed.set <- as.numeric(comb$stand.seed.set)

combnoseeds <- comb[comb$stand.seed.set > 0, ]
combnoseeds <- combnoseeds[is.na(combnoseeds$stand.seed.set) == "FALSE", ]

combnoseeds$ln.stand.seed.set <- log(combnoseeds$stand.seed.set)
```

## C. Graph! 

```{r}
compseedsetplot <- ggplot(data = combnoseeds, aes(x = area.leaf, y = ln.stand.seed.set, shape = type)) + 
  geom_smooth(aes(linetype = type,), method = "lm", color = "black", alpha = 0.2) + 
  scale_linetype_manual(values = c("solid", "dotdash")) + 
  geom_point(aes(color = treatment)) + 
  theme_bw() + 
  scale_color_manual(values = c("#1E88E5", "lime green", "orange", "#D81B60")) + 
  scale_shape_manual(values = c(16, 5)) + 
  labs(x = expression(paste("Leaf area consumed ", (m^{2}))), y = "Standardized seed set", 
       color = "Treatment group", linetype = "Hostplant", shape = "Hostplant")

compseedsetplot

ggsave("~/Desktop/GitHub/TBDCFit/Figures/EvolutionGraphs/compseedset.png", compseedsetplot, width = 8, 
       height = 5)
```

# 4. Rerun stats 

```{r}
modcompseedset <- lmer(ln.stand.seed.set ~ area.leaf*type + (1|column), data = combnoseeds)

summary(modcompseedset)

```

# 5. Run new stats on binary "did it make seeds?" metric

Gameplan: 

A. Use old dataset and write a for loop to add in "yes/no" seed production column
B. Run model 

## A. Write the loop 

Add in new column

```{r}
comb$any.seeds <- 0
```

```{r}
for(i in 1:length(unique(comb$pid))){
  if(is.na(comb[i, 11]) == "TRUE"){
    comb[i, 12] <- 0
  }else if(is.na(comb[i, 11]) == "FALSE"){
    comb[i, 12] <- 1
  }
}
```

## B. Run model

```{r}
anyseedsmod <- glmer(any.seeds ~ area.leaf* type + (1|column), data = comb, family = "binomial")

summary(anyseedsmod)
```

More tobacco failed to produce seeds, but herbivory level did not matter. 
