---
title: "Graphs and Analyses for Evolution"
output: html_notebook
---

This script makes graphs for my 2022 Evolution talk. 

Plan of attack: 

1) Make 3-level "theoretical" figure about expectations for herbivory
2) Make Histograms of herbivory by treatment group from the 2020 leaf scanner experiment 
3) Remake 2021 seed set graph to include all seed set plants (still excluding zeros)
4) Rerun stats on all seed set plants (excluding zeros still)
5) Run new stats on binary: did the plants produce seed? (By herbivory and plant type)


# 0. Load in packages

```{r}
library(dplyr)
library(ggplot2)
library(lmerTest)
```

# 1. Make theoretical figure with nice distributions to match results figure 

## Game plan: 

A. Come up with reasonable centers for each distribution
B. Make dataset with treatment, plant type, and different normal distributions for herbivory and seed set for the controls (centered on zero). 
C. Repeat for WAND, WE, WOWE
D. Graph it in increments to step through each treatment separately 


## A. Centers for distributions

CON (same for DC and TB): 
Herb: 0, SD 0 
Seed set: 0, SD 0.25

WAND
TB Herb: .25, SD .025
TB seed set: -1, SD .25
DC Herb: .25, SD .025
DC seed set: -1.25, SD .25

WE
TB Herb: .1, SD .025
TB seed set: -.5, SD .25
DC Herb: .1, SD .025
DC seed set: -.6, SD .25

WOWE
TB Herb: .5, SD .025
TB Seed set: -2, SD .25
DC Herb: .5, SD .025
DC Seed set: -2.5, SD .25


```{r}
set.seed(5)
```



## B. Make dataset for Controls

Some standardization: 10 datapoints per treatment group (for a total of 80)

```{r}
CONTB <- data.frame(
  pid = 1:10,
  treatment = "CON", 
  type = "TB", 
  herb = rnorm(10, mean = 0, sd = 0), 
  seedset = rnorm(10, mean = 0, sd = .25)
)
```

```{r}
CONDC <- data.frame(
  pid = 11:20,
  treatment = "CON", 
  type = "DC", 
  herb = rnorm(10, mean = 0, sd = 0), 
  seedset = rnorm(10, mean = 0, sd = .25)
)
```

```{r}
theodata <- rbind(CONTB, CONDC)
```


## C. Make for other three treatment groups


```{r}
WANDTB <- data.frame(
  pid = 21:30,
  treatment = "WAND", 
  type = "TB", 
  herb = rnorm(10, mean = 0.25, sd = 0.025), 
  seedset = rnorm(10, mean = -1, sd = .25)
)
```


```{r}
theodata <- rbind(theodata, WANDTB)
```


```{r}
WANDDC <- data.frame(
  pid = 31:40,
  treatment = "WAND", 
  type = "DC", 
  herb = rnorm(10, mean = 0.25, sd = 0.025), 
  seedset = rnorm(10, mean = -1.25, sd = .25)
)
```

```{r}
theodata <- rbind(theodata, WANDDC)
```



```{r}
WETB <- data.frame(
  pid = 41:50,
  treatment = "WE", 
  type = "TB", 
  herb = rnorm(10, mean = 0.1, sd = 0.025), 
  seedset = rnorm(10, mean = -.5, sd = .25)
)
```

```{r}
theodata <- rbind(theodata, WETB)
```

```{r}
WEDC <- data.frame(
  pid = 51:60,
  treatment = "WE", 
  type = "DC", 
  herb = rnorm(10, mean = 0.1, sd = 0.025), 
  seedset = rnorm(10, mean = -.6, sd = .25)
)
```

```{r}
theodata <- rbind(theodata, WEDC)
```



```{r}
WOWETB <- data.frame(
  pid = 61:70,
  treatment = "WOWE", 
  type = "TB", 
  herb = rnorm(10, mean = 0.5, sd = 0.025), 
  seedset = rnorm(10, mean = -2, sd = .25)
)
```

```{r}
theodata <- rbind(theodata, WOWETB)
```

```{r}
WOWEDC <- data.frame(
  pid = 71:80,
  treatment = "WOWE", 
  type = "DC", 
  herb = rnorm(10, mean = 0.5, sd = 0.025), 
  seedset = rnorm(10, mean = -2.5, sd = .25)
)
```

```{r}
theodata <- rbind(theodata, WOWEDC)
```

## D. Make incremental graphs

Total graph just to check: 

```{r}
totalplot <- ggplot(data = theodata, aes(x = herb, y = seedset, shape = type)) + 
  geom_smooth(aes(linetype = type), color = "black", method = "lm", alpha = 0.2) + 
  scale_linetype_manual(values = c("solid", "dotdash")) + 
  geom_point(aes(color = treatment)) + 
  theme_bw() + 
  ylim(-3.1, 0.6) + 
  xlim(0, .55) + 
  scale_color_manual(values = c("#1E88E5", "lime green", "orange", "#D81B60")) + 
  scale_shape_manual(values = c(16, 5)) + 
  labs(x = expression(paste("Leaf area consumed ", (m^{2}))), y = "Relative Fitness", 
       color = "Treatment group", shape = "Hostplant", linetype = "Hostplant") 

totalplot

ggsave("~/Desktop/GitHub/TBDCFit/Figures/EvolutionGraphs/totaltheo.png", totalplot, width = 8, height = 5)

```

We like it! Now on to each separate plot

WAND

```{r}
WANDplot <- ggplot(data = theodata[theodata$treatment == "CON" | theodata$treatment == "WAND", ], 
                   aes(x = herb, y = seedset, shape = type)) + 
  geom_point(aes(color = treatment)) + 
  theme_bw() + 
  ylim(-3.1, 0.6) + 
  xlim(0, .55) + 
  scale_color_manual(values = c("#1E88E5", "lime green")) + 
  scale_shape_manual(values = c(16, 5)) + 
  labs(x = expression(paste("Leaf area consumed ", (m^{2}))), y = "Relative Fitness", 
       color = "Treatment group", shape = "Hostplant") 

WANDplot

ggsave("~/Desktop/GitHub/TBDCFit/Figures/EvolutionGraphs/WANDtheo.png", WANDplot, width = 8, height = 5)

```

WE

```{r}
WEplot <- ggplot(data = theodata[theodata$treatment != "WOWE", ], aes(x = herb, y = seedset, shape = type)) + 
  geom_point(aes(color = treatment)) + 
  theme_bw() + 
  ylim(-3.1, 0.6) + 
  xlim(0, .55) + 
  scale_color_manual(values = c("#1E88E5", "lime green", "orange")) + 
  scale_shape_manual(values = c(16, 5)) + 
  labs(x = expression(paste("Leaf area consumed ", (m^{2}))), y = "Relative Fitness", 
       color = "Treatment group", shape = "Hostplant") 

WEplot

ggsave("~/Desktop/GitHub/TBDCFit/Figures/EvolutionGraphs/WEtheo.png", WEplot, width = 8, height = 5)

```

WOWE

```{r}
WOWEplot <- ggplot(data = theodata, aes(x = herb, y = seedset, shape = type)) + 
  geom_point(aes(color = treatment)) + 
  theme_bw() + 
  ylim(-3.1, 0.6) + 
  xlim(0, .55) + 
  scale_color_manual(values = c("#1E88E5", "lime green", "orange", "#D81B60")) + 
  scale_shape_manual(values = c(16, 5)) + 
  labs(x = expression(paste("Leaf area consumed ", (m^{2}))), y = "Relative Fitness", 
       color = "Treatment group", shape = "Hostplant") 

WOWEplot

ggsave("~/Desktop/GitHub/TBDCFit/Figures/EvolutionGraphs/WOWEtheo.png", WOWEplot, width = 8, height = 5)

```

# 2. Make histograms from leaf scanner expt. 

Game plan: 

A. Load in leaf scanner data
B. Calculate total herbivory using for loops 
C. Separate into columns I need (ID, treatment, type, total herbivory)
D. Make histograms with different fills by type in the same color for each treatment 


## A. Load in leaf scanner data and clean

```{r}
data <- read.csv("~/Desktop/MsCcHSFeedJan1MOD.csv")
scan <- read.csv("~/Desktop/MsCcHSFeedLeafScanFinal.csv", header = T)
```

```{r}
data <- data[data$fate != "dead" & data$fate != "quink" & data$fate != "wander*" & data$fate != "?", ]
data <- data[complete.cases(data[, 1]), ]
data$fate <- factor(data$fate, levels = c("wander", "em", "wowe", "wowe mongo"))

```


## B. Run the for loop


```{r}
#1
scan$comb <- paste(scan$Caterpillar.ID, "_", scan$Leaf.ID)

#0
unique <- unique(scan$comb)
consumed <- as.data.frame(unique)
consumed$area <- 0

#2-4
for (i in 1:length(consumed$unique)){
    subset <- filter(scan, scan$comb == consumed[i, 1])
    value <- max(subset$Leaf.Area) - min(subset$Leaf.Area)
    consumed[i, 2] <- value
}  

#5
consumed <- consumed %>%
  separate(unique, c("catID", "leafID"), "_")

#6
ID <- unique(consumed$catID)
consumedsum <- as.data.frame(ID)
consumedsum$totalarea <- 0

#7
for (i in 1:length(consumedsum$ID)){
  subset2 <- filter(consumed, consumed$catID == consumedsum[i, 1])
  value2 <- sum(subset2$area)
  consumedsum[i, 2] <- value2
}

#8
consumedsum$ID <- as.numeric(consumedsum$ID)

consumedsum <- consumedsum[consumedsum$ID %in% data$ID, ]

data <- data[data$ID %in% consumedsum$ID, ]

consumedsum <- consumedsum[order(consumedsum$ID), ]

data$area <- consumedsum$totalarea

data$area <- data$area / 10000

```


## C. Pare down into columns I need

```{r}
scandata <- data %>%
  select(ID, food, fate, area)
```

## D. Make histogram

WAND

```{r}
WANDhist <- ggplot(data = scandata[scandata$fate == "wander", ], aes(x = area)) + 
  geom_density(aes(fill = food), color = "lime green", position = "identity", alpha = 0.5) + 
  theme_bw() + 
  xlim(0, .6) + 
  scale_fill_manual(values = c("white", "lime green")) + 
  labs(x = expression(paste("Leaf area consumed ", (m^{2}))), y = "Frequency", fill = "Hostplant")

WANDhist

ggsave("~/Desktop/GitHub/TBDCFit/Figures/EvolutionGraphs/WANDhist.png", WANDhist, width = 8, height = 2)
```

WE

```{r}
WEhist <- ggplot(data = scandata[scandata$fate == "em", ], aes(x = area)) + 
  geom_density(aes(fill = food), color = "orange", position = "identity", alpha = 0.5) + 
  theme_bw() + 
  xlim(0, .6) + 
  scale_fill_manual(values = c("white", "orange")) + 
  labs(x = expression(paste("Leaf area consumed ", (m^{2}))), y = "Frequency", fill = "Hostplant")

WEhist

ggsave("~/Desktop/GitHub/TBDCFit/Figures/EvolutionGraphs/WEhist.png", WEhist, width = 8, height = 2)
```

WOWE

```{r}
WOWEhist <- ggplot(data = scandata[scandata$fate == "wowe mongo", ], aes(x = area)) + 
  geom_density(aes(fill = food), color = "#D81B60", position = "identity", alpha = 0.5) + 
  theme_bw() + 
  xlim(0, .6) + 
  scale_fill_manual(values = c("white", "#D81B60")) + 
  labs(x = expression(paste("Leaf area consumed ", (m^{2}))), y = "Frequency", fill = "Hostplant")

WOWEhist

ggsave("~/Desktop/GitHub/TBDCFit/Figures/EvolutionGraphs/WOWEhist.png", WOWEhist, width = 8, height = 2)
```