---
title: "Greenhouse summary graphs"
output: html_notebook
---

This script makes the summary graphs suggested by Joel on 11/8/22 to Anna. 

Roadmap:

0. Load in data and packages
1. For each metric (consumption, num flowers, num pods, num seeds germinated)
  a. Create collated metric 
  b. Graph separately (DC vs TB) as violin plots with jittered points
2. Plot fitness (num seeds germinated) vs. herbivory separately (DC vs TB)


# 0. Load in the data 

```{r}
library(tidyverse)
library(ggplot2)
library(lmerTest)
library(Rmisc)
```


```{r}
garea <- read.csv("~/Desktop/GitHub/TBDCFit/Data/Greenhouse/GreenLeafArea.csv", header = TRUE)
ggerm <- read.csv("~/Desktop/GitHub/TBDCFit/Data/Greenhouse/GreenGermCollated.csv", header = TRUE)
gkey <- read.csv("~/Desktop/GitHub/TBDCFit/Data/Greenhouse/GreenPIDTrtKey.csv", header = TRUE)
gpods <- read.csv("~/Desktop/GitHub/TBDCFit/Data/Greenhouse/GreenExitData.csv", header = TRUE)
gTBseed <- read.csv("~/Desktop/GitHub/TBDCFit/Data/Greenhouse/GreenTBSeed.csv", header = TRUE)
gDCseed <- read.csv("~/Desktop/GitHub/TBDCFit/Data/Greenhouse/GreenDCSeed.csv", header = TRUE)
gflowers <- read.csv("~/Desktop/GitHub/TBDCFit/Data/Greenhouse/GreenNumFlowers.csv", header = TRUE)
```

```{r}
gcolumn <- gkey %>%
  select(pid, column)

gcolumn$column <- as.factor(gcolumn$column)
```




# 1. Create metrics and graph 

## A. Consumption

### Create metric

Already completed - have treatment and type in `r garea`. 

### Graph

```{r}
greenann3 <- data.frame(label = c("A", "B"), 
                   type = c("DC", "TB"), 
                   treatment = NA)
```


```{r}
greenconsumpplot <- ggplot(aes(x = treatment, y = tot.area, color = treatment, shape = type), 
                           data = garea) + 
  theme_bw() + 
  geom_boxplot() + 
  #geom_point(alpha = 0.5, position = position_jitter(width = .2, height = 0)) + 
  labs(x = "Expected outcome", y = expression(paste("Total leaf area consumed ", (cm^{2})))
       ) + 
  scale_color_manual(values = c("black", "#1E88E5", "lime green", "#D81B60")) + 
  #scale_shape_manual(values = c(1, 16)) + 
  facet_wrap(~ type) + 
  geom_text(data = greenann3, aes(x = "CON", y = 8500, label = label), size = 10) + 
  theme(legend.position = "none")

greenconsumpplot
```

### Save graph

```{r}
ggsave("~/Desktop/GitHub/TBDCFit/Figures/Fig3green.png", greenconsumpplot, width = 8, height = 5)
```


**TRYING NEW PLOT IDEA 1/30**

```{r}
greenconsumpsum <- summarySE(data = garea, measurevar = "tot.area", 
                              groupvars = c("treatment", "type"))
```


```{r}
greenconsumpplotnew <- ggplot(aes(x = treatment, y = tot.area, shape = type, group = type), 
                           data = greenconsumpsum) + 
  theme_bw() + 
  geom_point(size = 3) + 
  geom_line(aes(linetype = type)) + 
  geom_errorbar(aes(ymin = tot.area - se, ymax = tot.area + se), width = 0.3)+ 
  labs(x = "Expected outcome", shape = "Hostplant type", group = "Hostplant type", 
       linetype = "Hostplant type") + 
  scale_shape_manual(values = c(1, 16)) + 
  scale_linetype_manual(values = c("dashed", "solid")) + 
  scale_y_continuous(expression(paste("Devil's claw leaf area consumed ", (cm^{2}))), 
                     sec.axis = sec_axis(~ . * 1, 
                                         name = expression(paste("Tobacco leaf area consumed ", (cm^{2}))))) + 
  #geom_text(aes(x = "CON", y = 6000, label = "A"), size = 10, color = "gray40") + 
  theme(legend.position = c(.2, .6))

greenconsumpplotnew
```



### Run stats

```{r}
garea <- merge(garea, gcolumn, by.x = "PID", by.y = "pid")
```


With column:
```{r}
gmodconsumpcol <- lmer(tot.area ~ treatment*type + (1|column), data = garea)

summary(gmodconsumpcol)
```

Column's variance is Zero - not necessary to include because it has no bearing on the consumption. 

Without column: 

```{r}
gmodconsump <- lm(tot.area ~ treatment*type, data = garea)

summary(gmodconsump)

anova(gmodconsump)
```


## B. Number of flowers

### Create metric

```{r}
gkey <- gkey %>%
  select(pid, type, treatment)

gflowers <- merge(gflowers, gkey, by = "pid")

```

### Graph

```{r}
greenannS1AB <- data.frame(label = c("A", "B"), 
                   type = c("DC", "TB"), 
                   treatment = NA, 
                   height = c(60, 209))
```


```{r}
greenflowerplot <- ggplot(aes(x = treatment, y = tot.flowers, color = treatment, shape = type), 
                           data = gflowers) + 
  theme_bw() + 
  geom_boxplot() + 
  #geom_point(alpha = 0.5, position = position_jitter(width = .2, height = 0)) + 
  labs(x = "Expected outcome", y = "Number of flowers produced" 
       ) + 
  scale_color_manual(values = c("black", "#1E88E5", "lime green", "#D81B60")) + 
  #scale_shape_manual(values = c(1, 16)) + 
  facet_wrap(~ type, scales = "free_y") +
  geom_text(data = greenannS1AB, aes(x = "WOWE", y = height, label = label), size = 10) + 
  theme(legend.position = "none")
  

greenflowerplot
```


### Save graph

```{r}
ggsave("~/Desktop/GitHub/TBDCFit/Figures/FigS1ABgreen.png", greenflowerplot, width = 8, height = 5)
```

**NEW GRAPH**

```{r}
gflowersum <- summarySE(data = gflowers, measurevar = "tot.flowers", 
                              groupvars = c("treatment", "type"))
```



```{r}
greenflowerplotnew <- ggplot(aes(x = treatment, shape = type, group = type), 
                           data = gflowersum[gflowersum$type == "DC", ]) + 
  theme_bw() + 
  geom_point(aes(y = tot.flowers), size = 3) + 
  geom_line(aes(y = tot.flowers, linetype = type)) + 
  geom_errorbar(aes(ymin = tot.flowers - se, ymax = tot.flowers + se), width = 0.3)+ 
  labs(x = "Expected outcome", shape = "Hostplant type", group = "Hostplant type", 
       linetype = "Hostplant type") + 
  scale_y_continuous("Devil's claw flowers produced", limits = c(0, 45), 
                     sec.axis = sec_axis(~ . * 4, name = "Tobacco flowers produced")) + 
  geom_point(aes(y = tot.flowers/4), data = gflowersum[gflowersum$type == "TB", ], size = 3) + 
  geom_line(aes(y = tot.flowers/4, linetype = type), data = gflowersum[gflowersum$type == "TB", ]) +
  geom_errorbar(aes(ymin = (tot.flowers/4 - se/4), ymax = (tot.flowers/4 + se/4)), width = 0.3, 
                data = gflowersum[gflowersum$type == "TB", ]) + 
  scale_shape_manual(values = c(1, 16)) + 
  scale_linetype_manual(values = c("dashed", "solid")) + 
  geom_text(aes(x = "WOWE", y = 40, label = "A"), size = 10, color = "gray40") + 
  theme(legend.position = c(0.2, 0.2))

greenflowerplotnew
```

```{r}
ggsave("~/Desktop/GitHub/TBDCFit/Figures/FigIntA.png", greenflowerplotnew, width = 8, height = 5)
```


### Run model

```{r}
gmodflow <- lm(tot.flowers ~ treatment*type, data = gflowers)

anova(gmodflow)
```



## C. Number of mature pods

### Create metric

```{r}
gpods <- gpods %>%
  select(pid, num.pods.m)

gpods <- merge(gpods, gkey, by = "pid")
```

### Graph

```{r}
greenannS1CD <- data.frame(label = c("C", "D"), 
                   type = c("DC", "TB"), 
                   treatment = NA, 
                   height = c(7.6, 130))
```


```{r}
greenpodsplot <- ggplot(aes(x = treatment, y = num.pods.m, color = treatment, shape = type), 
                           data = gpods) + 
  theme_bw() + 
  geom_boxplot() + 
  #geom_point(alpha = 0.5, position = position_jitter(width = .2, height = 0)) + 
  labs(x = "Expected outcome", y = "Number of mature pods produced"
       ) + 
  scale_color_manual(values = c("black", "#1E88E5", "lime green", "#D81B60")) + 
  #scale_shape_manual(values = c(1, 16)) + 
  facet_wrap(~ type, scales = "free_y") +
  geom_text(data = greenannS1CD, aes(x = "WOWE", y = height, label = label), size = 10) + 
  theme(legend.position = "none")

greenpodsplot
```

### Save graph

```{r}
ggsave("~/Desktop/GitHub/TBDCFit/Figures/FigS1CDgreen.png", greenpodsplot, width = 8, height = 5)
```

**NEW GRAPH**

```{r}
gpodssum <- summarySE(data = gpods, measurevar = "num.pods.m", 
                              groupvars = c("treatment", "type"))
```



```{r}
greenpodsplotnew <- ggplot(aes(x = treatment, shape = type, group = type), 
                           data = gpodssum[gpodssum$type == "DC", ]) + 
  theme_bw() + 
  geom_point(aes(y = num.pods.m), size = 3) + 
  geom_line(aes(y = num.pods.m, linetype = type)) + 
  geom_errorbar(aes(ymin = num.pods.m - se, ymax = num.pods.m + se), width = 0.3)+ 
  labs(x = "Expected outcome", shape = "Hostplant type", group = "Hostplant type", 
       linetype = "Hostplant type") + 
  scale_y_continuous("Devil's claw mature pods produced", limits = c(0, 9), 
                     sec.axis = sec_axis(~ . * 12, name = "Tobacco mature pods produced")) + 
  geom_point(aes(y = num.pods.m/12), data = gpodssum[gpodssum$type == "TB", ], size = 3) + 
  geom_line(aes(y = num.pods.m/12, linetype = type), data = gpodssum[gpodssum$type == "TB", ]) +
  geom_errorbar(aes(ymin = (num.pods.m/12 - se/12), ymax = (num.pods.m/12 + se/12)), width = 0.3, 
                data = gpodssum[gpodssum$type == "TB", ]) + 
  scale_shape_manual(values = c(1, 16)) + 
  scale_linetype_manual(values = c("dashed", "solid")) + 
  geom_text(aes(x = "WOWE", y = 8, label = "B"), size = 10, color = "gray40") + 
  theme(legend.position = "none")

greenpodsplotnew
```

```{r}
ggsave("~/Desktop/GitHub/TBDCFit/Figures/FigIntB.png", greenpodsplotnew, width = 8, height = 5)
```


### Run model

```{r}
gmodpods <- lm(num.pods.m ~ treatment*type, data = gpods)

anova(gmodpods)
```



## D. Seed set

### Create metric

Make for loop to count total number of DC seeds

```{r}
#1. List of unique PIDs in DCseed

DCpid <- unique(gDCseed$pid)

#2. Make output dataset

gDCseedout <- data.frame(pid = DCpid, 
                        seed.tot = 0)

#3. write the for loop 

for(i in 1:length(DCpid)){
  subset <- gDCseed[gDCseed$pid == DCpid[i], ]
  gDCseedout[i, 2] <- sum(subset$num.m.seeds)
}


```

Add in treatment groups

```{r}
gseedout <- merge(gDCseedout, gkey, all.y = TRUE, by = c("pid"))
```

Add in TB

```{r}
gTBseed <- merge(gTBseed, gpods, by.x = "PID", by.y = "pid")

gTBseed$seed.tot <- (gTBseed$Mass..g. / gTBseed$Total.Pods) * gTBseed$num.pods.m
```

Add in zeros

```{r}
gTBseed[gTBseed$PID == 241, 8] <- 0
gTBseed[gTBseed$PID == 271, 8] <- 0

gTBseed <- gTBseed %>%
  select(PID, seed.tot)
```

Merge with gseedout

```{r}
gseedout <- merge(gseedout, gTBseed, all.x = TRUE, by.x = c("pid"), by.y = c("PID"))
```


Add in zeros

```{r}
for(i in 1:length(gseedout$pid)){
  if(is.na(gseedout[i, 2]) == TRUE){
    gseedout[i, 2] <- 0
  } else if(is.na(gseedout[i, 2]) == FALSE){
    gseedout[i, 2] <- gseedout[i, 2]
  }
}


for(i in 1:length(gseedout$pid)){
  if(is.na(gseedout[i, 5]) == TRUE){
    gseedout[i, 5] <- 0
  } else if(is.na(gseedout[i, 5]) == FALSE){
    gseedout[i, 5] <- gseedout[i, 5]
  }
}

gseedout$seed.tot <- gseedout$seed.tot.x + gseedout$seed.tot.y

gseedout <- gseedout %>%
  select(pid, treatment, type, seed.tot)
```

Add in germination success

```{r}
ggerm <- ggerm %>%
  select(pid, prop.sprouted)


gseedout <- merge(gseedout, ggerm, all.x = TRUE, by = "pid")

for(i in 1:length(gseedout$pid)){
  if(is.na(gseedout[i, 5]) == TRUE){
    gseedout[i, 5] <- 0
  } else if(is.na(gseedout[i, 5]) == FALSE){
    gseedout[i, 5] <- gseedout[i, 5]
  }
}



gseedout$success <- gseedout$seed.tot * gseedout$prop.sprouted
```



### Graph

```{r}
greenannS1EF <- data.frame(label = c("E", "F"), 
                   type = c("DC", "TB"), 
                   treatment = NA, 
                   height = c(350, 35))
```


```{r}
greenseedplot <- ggplot(aes(x = treatment, y = seed.tot, color = treatment, shape = type), 
                           data = gseedout) + 
  theme_bw() + 
  geom_boxplot() + 
  #geom_point(alpha = 0.5, position = position_jitter(width = .2, height = 0)) + 
  labs(x = "Expected outcome", y = "Seed set" 
       ) + 
  scale_color_manual(values = c("black", "#1E88E5", "lime green", "#D81B60")) + 
  #scale_shape_manual(values = c(1, 16)) + 
  facet_wrap(~ type, scales = "free_y") +
  geom_text(data = greenannS1EF, aes(x = "WOWE", y = height, label = label), size = 10) + 
  theme(legend.position = "none")



greenseedplot
```

### Save graph

```{r}
ggsave("~/Desktop/GitHub/TBDCFit/Figures/FigS1EFgreen.png", greenseedplot, width = 8, height = 5)
```

**NEW PLOT**
```{r}
gseedssum <- summarySE(data = gseedout, measurevar = "seed.tot", 
                              groupvars = c("treatment", "type"))
```



```{r}
greenseedplotnew <- ggplot(aes(x = treatment, shape = type, group = type), 
                           data = gseedssum[gseedssum$type == "DC", ]) + 
  theme_bw() + 
  geom_point(aes(y = seed.tot), size = 3) + 
  geom_line(aes(y = seed.tot, linetype = type)) + 
  geom_errorbar(aes(ymin = seed.tot - se, ymax = seed.tot + se), width = 0.3)+ 
  labs(x = "Expected outcome", shape = "Hostplant type", group = "Hostplant type", 
       linetype = "Hostplant type") + 
  scale_y_continuous("Devil's claw seed set", limits = c(0, 225), 
                     sec.axis = sec_axis(~ . / 10, name = "Tobacco seed set")) + 
  geom_point(aes(y = seed.tot * 10), data = gseedssum[gseedssum$type == "TB", ], size = 3) + 
  geom_line(aes(y = seed.tot * 10, linetype = type), data = gseedssum[gseedssum$type == "TB", ]) +
  geom_errorbar(aes(ymin = (seed.tot * 10 - se * 10), ymax = (seed.tot * 10 + se * 10)), width = 0.3, 
                data = gseedssum[gseedssum$type == "TB", ]) + 
  scale_shape_manual(values = c(1, 16)) + 
  scale_linetype_manual(values = c("dashed", "solid")) + 
  geom_text(aes(x = "WOWE", y = 200, label = "C"), size = 10, color = "gray40") + 
  theme(legend.position = "none")

greenseedplotnew
```

```{r}
ggsave("~/Desktop/GitHub/TBDCFit/Figures/FigIntC.png", greenseedplotnew, width = 8, height = 5)
```


### Run model

```{r}
gmodseed <- lm(seed.tot ~ treatment*type, data = gseedout)

anova(gmodseed)
```


## E. Germination success

```{r}
greenannS1GH <- data.frame(label = c("G", "H"), 
                   type = c("DC", "TB"), 
                   treatment = NA, 
                   height = c(1.2, 1.2))
```

```{r}
greengermplot <- ggplot(aes(x = treatment, y = prop.sprouted, color = treatment, shape = type), 
                           data = gseedout) + 
  theme_bw() + 
  geom_boxplot() + 
  #geom_point(alpha = 0.5, position = position_jitter(width = .2, height = 0)) + 
  labs(x = "Expected outcome", y = "Germination Success" ) + 
  scale_color_manual(values = c("black", "#1E88E5", "lime green", "#D81B60")) + 
  #scale_shape_manual(values = c(1, 16)) + 
  facet_wrap(~ type) +
  ylim(0, 1.21) + 
  geom_text(data = greenannS1GH, aes(x = "WOWE", y = height, label = label), size = 10) + 
  theme(legend.position = "none")



greengermplot
```


### Save graph

```{r}
ggsave("~/Desktop/GitHub/TBDCFit/Figures/FigS1GHgreen.png", greengermplot, width = 8, height = 5)
```

**NEW PLOT**

```{r}
ggermsum <- summarySE(data = gseedout, measurevar = "prop.sprouted", 
                              groupvars = c("treatment", "type"))
```


```{r}
greengermplotnew <- ggplot(aes(x = treatment, y = prop.sprouted, shape = type, group = type), 
                           data = ggermsum) + 
  theme_bw() + 
  geom_point(size = 3) + 
  geom_line(aes(linetype = type)) + 
  geom_errorbar(aes(ymin = prop.sprouted - se, ymax = prop.sprouted + se), width = 0.3)+ 
  labs(x = "Expected outcome", shape = "Hostplant type", group = "Hostplant type", 
       linetype = "Hostplant type") + 
  scale_shape_manual(values = c(1, 16)) + 
  scale_linetype_manual(values = c("dashed", "solid")) + 
  scale_y_continuous("Devil's claw germination success", limits = c(0, 1), 
                     sec.axis = sec_axis(~ . * 1, 
                                         name = "Tobacco germination success")) + 
  geom_text(aes(x = "WOWE", y = .95, label = "D"), size = 10, color = "gray40") + 
  theme(legend.position = "none")

greengermplotnew
```

```{r}
ggsave("~/Desktop/GitHub/TBDCFit/Figures/FigIntD.png", greengermplotnew, width = 8, height = 5)
```


### Run model

```{r}
gmodgerm <- glm(prop.sprouted ~ treatment*type, data = gseedout, family = "binomial")

summary(gmodgerm)

anova(gmodgerm, test = "Chisq")
```


# 2. Fitness plot

Get into one dataset

```{r}
gfitness <- merge(garea, gseedout, by.x = c("PID", "treatment", "type"), by.y = c("pid", "treatment", "type"))
```

**NEW 1/26/23: Scale fitness to be relative fitness, with CON mean = 1**

```{r}
gfitness$rel.fitness <- 0

gfitness[gfitness$type == "DC", 9] <- (gfitness[gfitness$type == "DC", 8]) / (mean(gfitness[gfitness$treatment == "CON" & gfitness$type == "DC", 8]))

gfitness[gfitness$type == "TB", 9] <- (gfitness[gfitness$type == "TB", 8]) / (mean(gfitness[gfitness$treatment == "CON" & gfitness$type == "TB", 8]))
```




```{r}
greenann4 <- data.frame(label = c("A", "B"), 
                   type = c("DC", "TB"), 
                   treatment = NA, 
                   height = c(5, 5), 
                   width = c(3750, 8000))
```



```{r}
greenfitnessplot <- ggplot(aes(x = tot.area, y = rel.fitness), 
                           data = gfitness) + 
  theme_bw() +
  xlim(0, 8000) + 
  #ylim(0, 3) + 
  geom_smooth(aes(linetype = type), method = "lm", alpha = 0.2, color = "dark gray") +
  geom_point(aes(color = treatment, shape = type), alpha = 0.8, size = 2) + 
  labs(x = expression(paste("Total leaf area consumed ", (cm^{2}))), y = "Relative fitness", 
       color = "Expected outcome", shape = "Hostplant", linetype = "Hostplant") + 
  scale_color_manual(values = c("black", "#1E88E5", "lime green", "#D81B60")) + 
  scale_shape_manual(values = c(1, 16)) + 
  scale_linetype_manual(values = c("dashed", "solid")) + 
  theme(axis.text = element_text(size = 12), axis.title = element_text(size = 14), 
        legend.text = element_text(size = 12), legend.title = element_text(size = 14)) + 
  geom_text(aes(x = 7000, y = 2.75, label = "A"), size = 10, color = "gray40")
  #scale_y_continuous(limits=c(0,4.5), oob = scales::squish(x = , range = c(0, 4.5)))

greenfitnessplot
```

save plot: 
```{r}
ggsave("~/Desktop/GitHub/TBDCFit/Figures/Fig4greennew.png", greenfitnessplot, width = 8, height = 8)
```


```{r}
greenfitnessplotlog <- ggplot(aes(x = tot.area, y = log(rel.fitness + 0.01)), 
                           data = gfitness) + 
  theme_bw() +
  xlim(0, 8000) + 
  #ylim(0, 3) + 
  geom_smooth(aes(linetype = type), method = "lm", alpha = 0.2, color = "dark gray") +
  geom_point(aes(color = treatment, shape = type), alpha = 0.8) + 
  labs(x = expression(paste("Total leaf area consumed ", (cm^{2}))), y = "Relative fitness", 
       color = "Expected outcome", shape = "Hostplant", linetype = "Hostplant") + 
  scale_color_manual(values = c("black", "#1E88E5", "lime green", "#D81B60")) + 
  scale_shape_manual(values = c(1, 16)) + 
  scale_linetype_manual(values = c("dashed", "solid")) + 
  geom_text(aes(x = 7000, y = 2.75, label = "A"), size = 10, color = "gray40")
  #scale_y_continuous(limits=c(0,4.5), oob = scales::squish(x = , range = c(0, 4.5)))

greenfitnessplotlog
```





```{r}
greenfitnessplotpoly <- ggplot(aes(x = tot.area, y = rel.fitness), 
                           data = gfitness) + 
  theme_bw() +
  xlim(0, 8000) + 
  ylim(0, 3) + 
  stat_smooth(aes(linetype = type), method = lm, formula = y ~ poly(x, 2, raw = TRUE), alpha = 0.2, color = "dark gray") +
  geom_point(aes(color = treatment, shape = type), alpha = 0.8) + 
  labs(x = expression(paste("Total leaf area consumed ", (cm^{2}))), y = "Relative fitness", 
       color = "Expected outcome", shape = "Hostplant", linetype = "Hostplant") + 
  scale_color_manual(values = c("black", "#1E88E5", "lime green", "#D81B60")) + 
  scale_shape_manual(values = c(1, 16)) + 
  scale_linetype_manual(values = c("dashed", "solid")) + 
  geom_text(aes(x = 7000, y = 2.75, label = "A"), size = 10, color = "gray40")
  #scale_y_continuous(limits=c(0,4.5), oob = scales::squish(x = , range = c(0, 4.5)))

greenfitnessplotpoly
```

**Try scaling to median instead**

```{r}
gfitness$rel.fitness.med <- 0

gfitness[gfitness$type == "DC", 10] <- (gfitness[gfitness$type == "DC", 8]) / (median(gfitness[gfitness$treatment == "CON" & gfitness$type == "DC", 8]))

gfitness[gfitness$type == "TB", 10] <- (gfitness[gfitness$type == "TB", 8]) / (median(gfitness[gfitness$treatment == "CON" & gfitness$type == "TB", 8]))
```


```{r}
greenfitnessplotmed <- ggplot(aes(x = tot.area, y = rel.fitness.med), 
                           data = gfitness) + 
  theme_bw() +
  xlim(0, 8000) + 
  ylim(0, 4.5) + 
  geom_smooth(aes(linetype = type), method = "lm", alpha = 0.2, color = "dark gray") +
  geom_point(aes(color = treatment, shape = type), alpha = 0.8) + 
  labs(x = expression(paste("Total leaf area consumed ", (cm^{2}))), y = "Relative fitness", 
       color = "Expected outcome", shape = "Hostplant", linetype = "Hostplant") + 
  scale_color_manual(values = c("black", "#1E88E5", "lime green", "#D81B60")) + 
  scale_shape_manual(values = c(1, 16)) + 
  scale_linetype_manual(values = c("dashed", "solid")) + 
  geom_text(aes(x = 7000, y = 4.25, label = "A"), size = 10, color = "gray40")
  #scale_y_continuous(limits=c(0,4.5), oob = scales::squish(x = , range = c(0, 4.5)))

greenfitnessplotmed
```

```{r}
ggsave("~/Desktop/GitHub/TBDCFit/Figures/Fig4greenmedian.png", greenfitnessplotmed, width = 6, height = 5)
```





**For GRC poster and presentation:**

```{r}

```


```{r}
GRCfitnessplot <- ggplot(aes(x = tot.area, y = rel.fitness), data = gfitness) + 
  theme_bw() +
  xlim(0, 8000) + 
  #ylim(0, 3) + 
  geom_smooth(aes(linetype = type), method = "lm", alpha = 0.2, color = "dark gray") +
  geom_point(aes(color = treatment, shape = type), alpha = 0.8, size = 2) + 
  labs(x = expression(paste("Total leaf area consumed ", (cm^{2}))), y = "Relative fitness", 
       color = "Expected outcome", shape = "Hostplant", linetype = "Hostplant") + 
  scale_color_manual(values = c("#1E88E5", "lime green", "#FFA502", "#D81B60")) + 
  scale_shape_manual(values = c(19, 5)) + 
  scale_linetype_manual(values = c("solid", "dotdash")) + 
  theme(axis.text = element_text(size = 12), axis.title = element_text(size = 14), 
        legend.text = element_text(size = 12), legend.title = element_text(size = 14)) + 
  geom_text(aes(x = 2000, y = 2.75, label = "Greenhouse"), size = 10, color = "gray40") + 
  theme(legend.position = c(0.8, 0.8))

GRCfitnessplot
```

```{r}
ggsave("~/Desktop/GitHub/TBDCFit/Figures/GRCGreenCI.png", GRCfitnessplot, width = 8, height = 8)
```



Preliminary stats:

```{r}
greenfitmod1 <- lm(rel.fitness ~ tot.area*type, data = gfitness)

anova(greenfitmod1)
```

```{r}
greenfitmodlog <- lm(log(rel.fitness + 0.01) ~ tot.area*type, data = gfitness)

anova(greenfitmodlog)
```





```{r}
greenfitmod1med <- lm(rel.fitness.med ~ tot.area*type, data = gfitness)

anova(greenfitmod1med)
```

```{r}
greenfitmod2 <- lm(rel.fitness ~ treatment*type, data = gfitness)

anova(greenfitmod2)
```

```{r}
AIC(greenfitmod1, greenfitmod2)
```
Indistinguishable! Fun! 


Let's try with a polynomial fit instead

```{r}
greenfitmodpoly1 <- lm(rel.fitness ~ tot.area + I(tot.area^2) + type + tot.area:type, data = gfitness)

anova(greenfitmodpoly1)
```

```{r}
anova(greenfitmod1, greenfitmodpoly1)
```
```{r}
AIC(greenfitmod1, greenfitmodpoly1)
```


With column: 

```{r}
greenfitmod3 <- lmer(success ~ tot.area*type + (1|column), data = gfitness)

summary(greenfitmod3)
```

```{r}
greenfitmod4 <- lmer(success ~ treatment*type + (1|column), data = gfitness)

summary(greenfitmod4)
```





