---
title: "Floral Count Analysis for Greenhouse"
output: html_notebook
---

This script will calculate the total number of flowers pollinated on each plant for the entirety of the greenhouse study. 

Roadmap: 

0. Load in the data
1. Select relevant columns and create output file
2. Write a for loop to add floral number by PID
3. Create an output csv

# 0. Load in the data 

```{r}
library(tidyverse)
library(ggplot2)
library(Rmisc)
```


```{r}
pollgreen<- read.csv("~/Desktop/GitHub/TBDCFit/Data/Greenhouse/GreenPollination.csv", header = TRUE)
keygreen <- read.csv("~/Desktop/GitHub/TBDCFit/Data/Greenhouse/GreenPIDTrtKey.csv", header = TRUE)
exitgreen <- read.csv("~/Desktop/GitHub/TBDCFit/Data/Greenhouse/GreenExitData.csv", header = TRUE)
```

# 1. Select relevant columns 

```{r}
pollgreen <- pollgreen %>%
  select(date, pid, num.flowers)

pollgreen <- pollgreen[is.na(pollgreen$num.flowers) == FALSE, ]

keygreen <- keygreen %>%
  select(pid, type, treatment)

exitgreen <- exitgreen %>%
  select(pid, num.flower.unpol)


  
```

## Create an output file

```{r}
outputgreen <- data.frame(
  pid = unique(keygreen$pid),
  tot.flowers = 0
)

outputgreen <- outputgreen %>%
  arrange(pid)
```

# 2. Write the for loop 

1. Subset pollination data by PID
2. Take the sum of the num.flowers column
3. Stick that sum in the output file

```{r}
flowernum <- function(dataframe, output){
  
  for(i in 1:length(output$pid)){
    k <- output[i, 1]
    subset <- dataframe[dataframe$pid == k, ]
    output[i, 2] <- sum(subset$num.flowers)
  }
   return(output)
}
```

## Run the function

```{r}
outputgreen <- flowernum(dataframe = pollgreen, output = outputgreen)
```

## Merge with ending exit data - number of unpollinated flowers

```{r}
outputgreen <- merge(outputgreen, exitgreen, by = "pid")

outputgreen$tot.flowers <- outputgreen$tot.flowers + outputgreen$num.flower.unpol

outputgreen <- outputgreen %>%
  select(pid, tot.flowers)
```



# 3. Write to CSV 


```{r}
write.csv(x = outputgreen, file = "~/Desktop/GitHub/TBDCFit/Data/Greenhouse/GreenNumFlowers.csv", row.names = FALSE)
```




