---
title: "Greenhouse summary graphs"
output: html_notebook
---

This script makes the summary graphs suggested by Joel on 11/8/22 to Anna. 

Roadmap:

0. Load in data and packages
1. For each metric (consumption, num flowers, num pods, num seeds germinated)
  a. Create collated metric 
  b. Graph separately (DC vs TB) as violin plots with jittered points
2. Plot fitness (num seeds germinated) vs. herbivory separately (DC vs TB)


# 0. Load in the data 

```{r}
library(tidyverse)
library(ggplot2)
```


```{r}
garea <- read.csv("~/Desktop/GitHub/TBDCFit/Data/Greenhouse/GreenLeafArea.csv", header = TRUE)
ggerm <- read.csv("~/Desktop/GitHub/TBDCFit/Data/Greenhouse/GreenGermCollated.csv", header = TRUE)
gkey <- read.csv("~/Desktop/GitHub/TBDCFit/Data/Greenhouse/GreenPIDTrtKey.csv", header = TRUE)
gpods <- read.csv("~/Desktop/GitHub/TBDCFit/Data/Greenhouse/GreenExitData.csv", header = TRUE)
gTBseed <- read.csv("~/Desktop/GitHub/TBDCFit/Data/Greenhouse/GreenTBSeed.csv", header = TRUE)
gDCseed <- read.csv("~/Desktop/GitHub/TBDCFit/Data/Greenhouse/GreenDCSeed.csv", header = TRUE)
gflowers <- read.csv("~/Desktop/GitHub/TBDCFit/Data/Greenhouse/GreenNumFlowers.csv", header = TRUE)
```

# 1. Create metrics and graph 

## A. Consumption

### Create metric

Already completed - have treatment and type in `r garea`. 

### Graph

```{r}
greenconsumpplot <- ggplot(aes(x = treatment, y = tot.area, color = treatment, shape = type), 
                           data = garea) + 
  theme_bw() + 
  geom_boxplot() + 
  #geom_point(alpha = 0.5, position = position_jitter(width = .2, height = 0)) + 
  labs(x = "Treatment group", y = expression(paste("Total leaf area consumed ", (cm^{2}))), 
       color = "Treatment", fill = "Treatment", shape = "Hostplant") + 
  scale_color_manual(values = c("black", "#1E88E5", "lime green", "#D81B60")) + 
  #scale_shape_manual(values = c(1, 16)) + 
  facet_wrap(~ type) + 
  theme(legend.position = "none")

greenconsumpplot
```

### Save graph

```{r}

```


## B. Number of flowers

### Create metric

```{r}
gkey <- gkey %>%
  select(pid, type, treatment)

gflowers <- merge(gflowers, gkey, by = "pid")

```

### Graph

```{r}
greenflowerplot <- ggplot(aes(x = treatment, y = tot.flowers, color = treatment, shape = type), 
                           data = gflowers) + 
  theme_bw() + 
  geom_boxplot() + 
  #geom_point(alpha = 0.5, position = position_jitter(width = .2, height = 0)) + 
  labs(x = "Treatment group", y = "Number of flowers produced", 
       color = "Treatment", fill = "Treatment", shape = "Hostplant") + 
  scale_color_manual(values = c("black", "#1E88E5", "lime green", "#D81B60")) + 
  #scale_shape_manual(values = c(1, 16)) + 
  facet_wrap(~ type, scales = "free_y") +
  theme(legend.position = "none")
  

greenflowerplot
```


### Save graph

```{r}

```


## C. Number of mature pods

### Create metric

```{r}
gpods <- gpods %>%
  select(pid, num.pods.m)

gpods <- merge(gpods, gkey, by = "pid")
```

### Graph

```{r}
greenpodsplot <- ggplot(aes(x = treatment, y = num.pods.m, color = treatment, shape = type), 
                           data = gpods) + 
  theme_bw() + 
  geom_boxplot() + 
  #geom_point(alpha = 0.5, position = position_jitter(width = .2, height = 0)) + 
  labs(x = "Treatment group", y = "Number of mature pods produced", 
       color = "Treatment", fill = "Treatment", shape = "Hostplant") + 
  scale_color_manual(values = c("black", "#1E88E5", "lime green", "#D81B60")) + 
  #scale_shape_manual(values = c(1, 16)) + 
  facet_wrap(~ type, scales = "free_y") +
  theme(legend.position = "none")

greenpodsplot
```

### Save graph

```{r}

```


## D. Seeds germinated

### Create metric

Make for loop to count total number of DC seeds

```{r}
#1. List of unique PIDs in DCseed

DCpid <- unique(gDCseed$pid)

#2. Make output dataset

gDCseedout <- data.frame(pid = DCpid, 
                        seed.tot = 0)

#3. write the for loop 

for(i in 1:length(DCpid)){
  subset <- gDCseed[gDCseed$pid == DCpid[i], ]
  gDCseedout[i, 2] <- sum(subset$num.m.seeds)
}


```

Add in treatment groups

```{r}
gseedout <- merge(gDCseedout, gkey, all.y = TRUE, by = c("pid", "treatment", "type"))
```

Add in TB

```{r}
gTBseed <- merge(gTBseed, gpods, by.x = "PID", by.y = "pid")

gTBseed$seed.tot <- (gTBseed$Mass..g. / gTBseed$Total.Pods) * gTBseed$num.pods.m
```

Add in zeros

```{r}
gTBseed[gTBseed$PID == 241, 8] <- 0
gTBseed[gTBseed$PID == 271, 8] <- 0

gTBseed <- gTBseed %>%
  select(PID, seed.tot)
```

Merge with gseedout

```{r}
gseedout <- merge(gseedout, gTBseed, all.x = TRUE, by.x = c("pid"), by.y = c("PID"))
```


Add in zeros

```{r}
for(i in 1:length(gseedout$pid)){
  if(is.na(gseedout[i, 4]) == TRUE){
    gseedout[i, 4] <- 0
  } else if(is.na(gseedout[i, 4]) == FALSE){
    gseedout[i, 4] <- gseedout[i, 4]
  }
}


for(i in 1:length(gseedout$pid)){
  if(is.na(gseedout[i, 5]) == TRUE){
    gseedout[i, 5] <- 0
  } else if(is.na(gseedout[i, 5]) == FALSE){
    gseedout[i, 5] <- gseedout[i, 5]
  }
}

gseedout$seed.tot <- gseedout$seed.tot.x + gseedout$seed.tot.y

gseedout <- gseedout %>%
  select(pid, treatment, type, seed.tot)
```

Add in germination success

```{r}
ggerm <- ggerm %>%
  select(pid, prop.sprouted)


gseedout <- merge(gseedout, ggerm, all.x = TRUE, by = "pid")

for(i in 1:length(gseedout$pid)){
  if(is.na(gseedout[i, 5]) == TRUE){
    gseedout[i, 5] <- 0
  } else if(is.na(gseedout[i, 5]) == FALSE){
    gseedout[i, 5] <- gseedout[i, 5]
  }
}



gseedout$success <- gseedout$seed.tot * gseedout$prop.sprouted
```



### Graph

```{r}
greenseedplot <- ggplot(aes(x = treatment, y = success, color = treatment, shape = type), 
                           data = gseedout) + 
  theme_bw() + 
  geom_boxplot() + 
  #geom_point(alpha = 0.5, position = position_jitter(width = .2, height = 0)) + 
  labs(x = "Treatment group", y = "Amount of viable seed produced", 
       color = "Treatment", fill = "Treatment", shape = "Hostplant") + 
  #scale_color_manual(values = c("black", "#1E88E5", "lime green", "#D81B60")) + 
  scale_shape_manual(values = c(1, 16)) + 
  facet_wrap(~ type, scales = "free_y") 

greenseedplot
```

### Save graph

```{r}

```


# 2. Fitness plot

Get into one dataset

```{r}
gfitness <- merge(garea, gseedout, by.x = c("PID", "treatment", "type"), by.y = c("pid", "treatment", "type"))
```


```{r}
greenfitnessplot <- ggplot(aes(x = tot.area, y = success), 
                           data = gfitness) + 
  theme_bw() + 
  geom_smooth(method = "lm", alpha = 0.2, color = "dark gray") +
  geom_point(aes(color = treatment, shape = type), alpha = 0.8) + 
  labs(x = expression(paste("Total leaf area consumed ", (cm^{2}))), y = "Fitness", 
       color = "Treatment", shape = "Hostplant") + 
  scale_color_manual(values = c("black", "#1E88E5", "lime green", "#D81B60")) + 
  scale_shape_manual(values = c(1, 16)) + 
  facet_wrap(~ type, scales = "free") 

greenfitnessplot
```


Preliminary stats:

```{r}
greenfitmod1 <- lm(success ~ tot.area*type, data = gfitness)

anova(greenfitmod1)
```


```{r}
greenfitmod2 <- lm(success ~ treatment*type, data = gfitness)

anova(greenfitmod2)
```

