---
title: "Summary Table Code for Greenhouse"
output: html_notebook
---

This script will make the summary table to include in the manuscript. 

Contents: 

1. % plants with flowers
  - extract which plants had any flowers from final flowering datasheet
2. # flowers / plant
  - take the mean of those with flowers by trt and type
3. % plants with mature pods
  - extract which plants had any pods from final pod datasheet
4. # pods / plant
  - take the mean of those with mature pods by trt and type
5. #/mass of seeds / pod
  - take the mean of those by trt and type
6. % seeds germinated
  - take the mean of those who we germinated from by trt and type
7. area of leaves consumed
  - take the mean from final herbivory datasheet

Roadmap: 

0. Load in packages and datasets
1. Make output file
2. Go through 1-6 each in order, adding to an output datafile. 
3. Export output datafile as a csv. 


# 0. Load in our packages and datasets 

```{r}
library(tidyverse)
library(Rmisc)
library(ggplot2)
```

## FIELD: 

```{r}
garea <- read.csv("~/Desktop/GitHub/TBDCFit/Data/Greenhouse/GreenLeafArea.csv", header = TRUE)
#ggerm <- read.csv("~/Desktop/GitHub/TBDCFit/Data/Greenhouse/GermCollated.csv", header = TRUE)
gkey <- read.csv("~/Desktop/GitHub/TBDCFit/Data/Greenhouse/GreenPIDTrtKey.csv", header = TRUE)
gpods <- read.csv("~/Desktop/GitHub/TBDCFit/Data/Greenhouse/GreenExitData.csv", header = TRUE)
gTBseed <- read.csv("~/Desktop/GitHub/TBDCFit/Data/Greenhouse/GreenTBSeed.csv", header = TRUE)
gDCseed <- read.csv("~/Desktop/GitHub/TBDCFit/Data/Greenhouse/GreenDCSeed.csv", header = TRUE)
gflowers <- read.csv("~/Desktop/GitHub/TBDCFit/Data/Greenhouse/GreenNumFlowers.csv", header = TRUE)
```


# 1. Output file

```{r}
metrics <- c("percentflowers", "numflowers", "percentpods", "numpods", "numseeds", "percentgerm", "leafarea")

goutput <- data.frame(metric = metrics, 
                     N = 0, 
                     DCCONmean = 0, 
                     DCCONse = 0, 
                     DCWANDmean = 0, 
                     DCWANDse = 0,
                     DCWEmean = 0, 
                     DCWEse = 0,
                     DCWOWEmean = 0, 
                     DCWOWEse = 0,
                     TBCONmean = 0, 
                     TBCONse = 0, 
                     TBWANDmean = 0, 
                     TBWANDse = 0,
                     TBWEmean = 0, 
                     TBWEse = 0,
                     TBWOWEmean = 0, 
                     TBWOWEse = 0)
```


# 2. Go through each metric

## 1. Percent flowers

Datafile: output of for loop (gflowers), key (gkey)
Approach: Create binary column, subset by Trt+Type, take number of 1s over total number


get requisite columns in dataframe

```{r}
gkey <- gkey %>%
  select(pid, type, treatment)

gflowers <- merge(gflowers, gkey, by = "pid")

gflowers$binary <- 0

gflowers$composite <- paste(gflowers$type, gflowers$treatment, sep = " ")
```

for loop for binary assignment 

```{r}
for(i in 1:length(gflowers$pid)){
  if(gflowers[i, 2] > 0){
    gflowers[i, 5] <- 1
  } else if(gflowers[i, 2] <= 0){
    gflowers[i, 5] <- 0
  }
}

```

for loop for subsetting and getting percentages

```{r}
gflowperc <- data.frame(composite = unique(gflowers$composite), 
                        perc = 0)

gflowperc <- gflowperc[order(gflowperc$composite), ]

uniquecomp <- gflowperc$composite

for(i in 1:length(uniquecomp)){
  k <- uniquecomp[[i]]
  subset <- gflowers[gflowers$composite == k, ]
  #print(subset)
  gflowperc[gflowperc$composite == k, 2] <- (sum(subset$binary)) / (length(subset$binary))
}
```

Add to output table

```{r}
goutput[1, 2] <- 80

goutput[1, 3] <- gflowperc[1, 2]
goutput[1, 5] <- gflowperc[2, 2]
goutput[1, 7] <- gflowperc[3, 2]
goutput[1, 9] <- gflowperc[4, 2]
goutput[1, 11] <- gflowperc[5, 2]
goutput[1, 13] <- gflowperc[6, 2]
goutput[1, 15] <- gflowperc[7, 2]
goutput[1, 17] <- gflowperc[8, 2]
```