---
title: "Summary Table Code for Greenhouse"
output: html_notebook
---

This script will make the summary table to include in the manuscript. 

Contents: 

1. % plants with flowers
  - extract which plants had any flowers from final flowering datasheet
2. # flowers / plant
  - take the mean of those with flowers by trt and type
3. % plants with mature pods
  - extract which plants had any pods from final pod datasheet
4. # pods / plant
  - take the mean of those with mature pods by trt and type
5. #/mass of seeds / pod
  - take the mean of those by trt and type
6. % seeds germinated
  - take the mean of those who we germinated from by trt and type
7. area of leaves consumed
  - take the mean from final herbivory datasheet

Roadmap: 

0. Load in packages and datasets
1. Make output file
2. Go through 1-6 each in order, adding to an output datafile. 
3. Export output datafile as a csv. 


# 0. Load in our packages and datasets 

```{r}
library(tidyverse)
library(Rmisc)
library(ggplot2)
```


```{r}
garea <- read.csv("~/Desktop/GitHub/TBDCFit/Data/Greenhouse/GreenLeafArea.csv", header = TRUE)
ggerm <- read.csv("~/Desktop/GitHub/TBDCFit/Data/Greenhouse/GreenGermCollated.csv", header = TRUE)
gkey <- read.csv("~/Desktop/GitHub/TBDCFit/Data/Greenhouse/GreenPIDTrtKey.csv", header = TRUE)
gpods <- read.csv("~/Desktop/GitHub/TBDCFit/Data/Greenhouse/GreenExitData.csv", header = TRUE)
gTBseed <- read.csv("~/Desktop/GitHub/TBDCFit/Data/Greenhouse/GreenTBSeed.csv", header = TRUE)
gDCseed <- read.csv("~/Desktop/GitHub/TBDCFit/Data/Greenhouse/GreenDCSeed.csv", header = TRUE)
gflowers <- read.csv("~/Desktop/GitHub/TBDCFit/Data/Greenhouse/GreenNumFlowers.csv", header = TRUE)
```


# 1. Output file

```{r}
metrics <- c("percentflowers", "numflowers", "percentpods", "numpods", "numseeds", "percentgerm", "leafarea")

goutput <- data.frame(metric = metrics, 
                     N = 0, 
                     DCCONmean = 0, 
                     DCCONse = 0, 
                     DCWANDmean = 0, 
                     DCWANDse = 0,
                     DCWEmean = 0, 
                     DCWEse = 0,
                     DCWOWEmean = 0, 
                     DCWOWEse = 0,
                     TBCONmean = 0, 
                     TBCONse = 0, 
                     TBWANDmean = 0, 
                     TBWANDse = 0,
                     TBWEmean = 0, 
                     TBWEse = 0,
                     TBWOWEmean = 0, 
                     TBWOWEse = 0)
```


# 2. Go through each metric

## 1. Percent flowers

Datafile: output of for loop (gflowers), key (gkey)
Approach: Create binary column, subset by Trt+Type, take number of 1s over total number


get requisite columns in dataframe

```{r}
gkey <- gkey %>%
  select(pid, type, treatment)

gflowers <- merge(gflowers, gkey, by = "pid")

gflowers$binary <- 0

gflowers$composite <- paste(gflowers$type, gflowers$treatment, sep = " ")
```

for loop for binary assignment 

```{r}
for(i in 1:length(gflowers$pid)){
  if(gflowers[i, 2] > 0){
    gflowers[i, 5] <- 1
  } else if(gflowers[i, 2] <= 0){
    gflowers[i, 5] <- 0
  }
}

```

for loop for subsetting and getting percentages

```{r}
gflowperc <- data.frame(composite = unique(gflowers$composite), 
                        perc = 0)

gflowperc <- gflowperc[order(gflowperc$composite), ]

uniquecomp <- gflowperc$composite

for(i in 1:length(uniquecomp)){
  k <- uniquecomp[[i]]
  subset <- gflowers[gflowers$composite == k, ]
  #print(subset)
  gflowperc[gflowperc$composite == k, 2] <- (sum(subset$binary)) / (length(subset$binary))
}
```

Add to output table

```{r}
goutput[1, 2] <- 80

goutput[1, 3] <- gflowperc[1, 2]
goutput[1, 5] <- gflowperc[2, 2]
goutput[1, 7] <- gflowperc[3, 2]
goutput[1, 9] <- gflowperc[4, 2]
goutput[1, 11] <- gflowperc[5, 2]
goutput[1, 13] <- gflowperc[6, 2]
goutput[1, 15] <- gflowperc[7, 2]
goutput[1, 17] <- gflowperc[8, 2]
```

## 2. Number of flowers per plant

Data: output of total flowers (gflowers)
Approach: subset by those that flowered, then summarySE 

```{r}
gflowersyes <- gflowers[gflowers$binary == 1, ]

gtotflow <- summarySE(data = gflowersyes,
                      measurevar = "tot.flowers", 
                      groupvars = "composite")
```

Add to final output 

```{r}
goutput[2, 2] <- sum(gtotflow$N)

goutput[2, 3] <- gtotflow[1, 3]
goutput[2, 4] <- gtotflow[1, 5]
goutput[2, 5] <- gtotflow[2, 3]
goutput[2, 6] <- gtotflow[2, 5]
goutput[2, 7] <- gtotflow[3, 3]
goutput[2, 8] <- gtotflow[3, 5]
goutput[2, 9] <- gtotflow[4, 3]
goutput[2, 10] <- gtotflow[4, 5]
goutput[2, 11] <- gtotflow[5, 3]
goutput[2, 12] <- gtotflow[5, 5]
goutput[2, 13] <- gtotflow[6, 3]
goutput[2, 14] <- gtotflow[6, 5]
goutput[2, 15] <- gtotflow[7, 3]
goutput[2, 16] <- gtotflow[7, 5]
goutput[2, 17] <- gtotflow[8, 3]
goutput[2, 18] <- gtotflow[8, 5]

```
## 3. Percent with mature pods

Data: pods datasheets (gpods) + key (gkey)
Approach: get rid of misc columns, create binary, calculate percentage 

```{r}
gpods <- gpods %>%
  select(pid, num.pods.m)

gpods <- merge(gpods, gkey, by.x = "pid", by.y = "pid")

gpods$binary <- 0

gpods$composite <- paste(gpods$type, gpods$treatment, sep = " ")


```

```{r}
for(i in 1:length(gpods$pid)){
  if(gpods[i, 2] > 0){
    gpods[i, 5] <- 1
  } else if(gpods[i, 2] <= 0){
    gpods[i, 5] <- 0
  }
}

```

for loop for getting pod counts


```{r}
gpodperc <- data.frame(composite = unique(gpods$composite), 
                        perc = 0)

gpodperc <- gpodperc[order(gpodperc$composite), ]

for(i in 1:length(uniquecomp)){
  k <- uniquecomp[[i]]
  subset <- gpods[gpods$composite == k, ]
  #print(subset)
  gpodperc[gpodperc$composite == k, 2] <- (sum(subset$binary)) / (length(subset$binary))
}
```
put in output table


```{r}
goutput[3, 2] <- 80

goutput[3, 3] <- gpodperc[1, 2]
goutput[3, 5] <- gpodperc[2, 2]
goutput[3, 7] <- gpodperc[3, 2]
goutput[3, 9] <- gpodperc[4, 2]
goutput[3, 11] <- gpodperc[5, 2]
goutput[3, 13] <- gpodperc[6, 2]
goutput[3, 15] <- gpodperc[7, 2]
goutput[3, 17] <- gpodperc[8, 2]
```


## 4. Number of pods per plant

Data: output of total pods (gpods)
Approach: subset by those that had mature pods, then summarySE 

```{r}
gpodsyes <- gpods[gpods$binary == 1, ]

gtotpod <- summarySE(data = gpodsyes,
                      measurevar = "num.pods.m", 
                      groupvars = "composite")
```

```{r}
goutput[4, 2] <- sum(gtotpod$N)

goutput[4, 3] <- gtotpod[1, 3]
goutput[4, 4] <- gtotpod[1, 5]
goutput[4, 5] <- gtotpod[2, 3]
goutput[4, 6] <- gtotpod[2, 5]
goutput[4, 7] <- gtotpod[3, 3]
goutput[4, 8] <- gtotpod[3, 5]
goutput[4, 9] <- gtotpod[4, 3]
goutput[4, 10] <- gtotpod[4, 5]
goutput[4, 11] <- gtotpod[5, 3]
goutput[4, 12] <- gtotpod[5, 5]
goutput[4, 13] <- gtotpod[6, 3]
goutput[4, 14] <- gtotpod[6, 5]
goutput[4, 15] <- gtotpod[7, 3]
goutput[4, 16] <- gtotpod[7, 5]
goutput[4, 17] <- gtotpod[8, 3]
goutput[4, 18] <- gtotpod[8, 5]

```
## 5. Amount of seeds per pod - COME BACK TO THIS

Data: gTBseed, gDCseed, gkey
Approach: Exclude those without pods or that we couldn't measure, use fitness code to get average seed mass/number per plant, then use summarySE to get by treatment group

**Take seed pod mass off of each individual, then average**

Make a binary column for holes in TB pods

```{r}
gTBseed$binary <- 0
```

```{r}
for(i in 1:length(gTBseed$PID)){
  if(gTBseed[i, 3] > 0){
    gTBseed[i, 5] <- 1
  } else if(gTBseed[i, 3] <= 0){
    gTBseed[i, 5] <- 0
  }
}

```
Seed mass per TB pod 


```{r}
gTBseed$mass.per.pod <- gTBseed$Mass..g. / gTBseed$Total.Pods
```

Remove unnecessary columns fromm TBseed

```{r}
gTBseed <- gTBseed %>%
  select(pid = PID, binary = binary, per.pod = mass.per.pod)
```

Account for TB plants without mature pods

```{r}
gTBseed <- gTBseed[gTBseed$pid!=241,] 
gTBseed <- gTBseed[gTBseed$pid!=271,] 
```


### Write a for loop to get avg seed number per pod for DC

```{r}
#1. List of unique PIDs in DCseed

gDCpid <- unique(gDCseed$pid)

#2. Make output dataset

gDCseedout <- data.frame(pid = gDCpid, 
                        pod.avg = 0)

#3. write the for loop 

for(i in 1:length(gDCpid)){
  subset <- gDCseed[gDCseed$pid == gDCpid[i], ]
  gDCseedout[i, 2] <- mean(subset$num.m.seeds)
}
```

**Combine datafiles**

```{r}
gDCseedout$binary <- 0 #just adding in because none had spodoptera damage

gDCseedout <- gDCseedout %>%
  select(pid, binary, per.pod = pod.avg)
```

```{r}
gperpod <- rbind(gTBseed, gDCseedout)
```

**Add in treatment group**

```{r}
gperpod <- merge(gperpod, gkey, by = "pid")
gperpod$composite <- paste(gperpod$type, gperpod$treatment, sep = " ")
```

**summarySE**

```{r}
gperpodsum <- summarySE(data = gperpod, 
                        measurevar = "per.pod", 
                        groupvars = "composite")
```

**Input into table**

```{r}
goutput[5, 2] <- sum(gperpodsum$N)

goutput[5, 3] <- gperpodsum[1, 3]
goutput[5, 4] <- gperpodsum[1, 5]
goutput[5, 5] <- gperpodsum[2, 3]
goutput[5, 6] <- gperpodsum[2, 5]
goutput[5, 7] <- gperpodsum[3, 3]
goutput[5, 8] <- gperpodsum[3, 5]
goutput[5, 9] <- gperpodsum[4, 3]
goutput[5, 10] <- gperpodsum[4, 5]
goutput[5, 11] <- gperpodsum[5, 3]
goutput[5, 12] <- gperpodsum[5, 5]
goutput[5, 13] <- gperpodsum[6, 3]
goutput[5, 14] <- gperpodsum[6, 5]
goutput[5, 15] <- gperpodsum[7, 3]
goutput[5, 16] <- gperpodsum[7, 5]
goutput[5, 17] <- gperpodsum[8, 3]
goutput[5, 18] <- gperpodsum[8, 5]
```

## 6. Percent germination 

Data: ggerm, gkey
Approach: summarySE

```{r}
ggerm <- merge(ggerm, gkey, by = "pid")

ggerm$composite <- paste(ggerm$type, ggerm$treatment, sep = " ")
```


```{r}
ggermperc <- summarySE(data = ggerm, 
                       measurevar = "prop.sprouted", 
                       groupvars = "composite")


```

Input into summary table

```{r}
goutput[6, 2] <- sum(ggermperc$N)

goutput[6, 3] <- ggermperc[1, 3]
goutput[6, 4] <- ggermperc[1, 5]
goutput[6, 5] <- ggermperc[2, 3]
goutput[6, 6] <- ggermperc[2, 5]
goutput[6, 7] <- ggermperc[3, 3]
goutput[6, 8] <- ggermperc[3, 5]
goutput[6, 9] <- ggermperc[4, 3]
goutput[6, 10] <- ggermperc[4, 5]
goutput[6, 11] <- ggermperc[5, 3]
goutput[6, 12] <- ggermperc[5, 5]
goutput[6, 13] <- ggermperc[6, 3]
goutput[6, 14] <- ggermperc[6, 5]
goutput[6, 15] <- ggermperc[7, 3]
goutput[6, 16] <- ggermperc[7, 5]
goutput[6, 17] <- ggermperc[8, 3]
goutput[6, 18] <- ggermperc[8, 5]
```

## 7. Leaf Area
Data: garea
Approach: summarySE

```{r}
garea$composite <- paste(garea$type, garea$treatment, sep = " ")
```


```{r}
gtotarea <- summarySE(data = garea, 
                       measurevar = "tot.area", 
                       groupvars = "composite")


```

Input into summary table

```{r}
goutput[7, 2] <- 80

goutput[7, 3] <- gtotarea[1, 3]
goutput[7, 4] <- gtotarea[1, 5]
goutput[7, 5] <- gtotarea[2, 3]
goutput[7, 6] <- gtotarea[2, 5]
goutput[7, 7] <- gtotarea[3, 3]
goutput[7, 8] <- gtotarea[3, 5]
goutput[7, 9] <- gtotarea[4, 3]
goutput[7, 10] <- gtotarea[4, 5]
goutput[7, 11] <- gtotarea[5, 3]
goutput[7, 12] <- gtotarea[5, 5]
goutput[7, 13] <- gtotarea[6, 3]
goutput[7, 14] <- gtotarea[6, 5]
goutput[7, 15] <- gtotarea[7, 3]
goutput[7, 16] <- gtotarea[7, 5]
goutput[7, 17] <- gtotarea[8, 3]
goutput[7, 18] <- gtotarea[8, 5]
```

```{r}
write.csv(x = goutput, file = "~/Desktop/GitHub/TBDCFit/Data/Greenhouse/GreenSummaryTable.csv", row.names = FALSE)
```


