---
title: "Greenhouse Fitness Analysis"
output: html_notebook
---


This script calculates fitness for the greenhouse experiment. 

Roadmap: 

0. Load in the data and packages
1. Get seed set per plant
2. Standardize to the control group
3. Combine with germination success
4. Graph
5. Run statistical analysis 

# 0. Load in packages and data

```{r}
library(tidyverse)
library(ggplot2)
#library(lme4)
library(lmerTest)
```


```{r}
garea <- read.csv("~/Desktop/GitHub/TBDCFit/Data/Greenhouse/GreenLeafArea.csv", header = TRUE)
ggerm <- read.csv("~/Desktop/GitHub/TBDCFit/Data/Greenhouse/GreenGermCollated.csv", header = TRUE)
gkey <- read.csv("~/Desktop/GitHub/TBDCFit/Data/Greenhouse/GreenPIDTrtKey.csv", header = TRUE)
gpods <- read.csv("~/Desktop/GitHub/TBDCFit/Data/Greenhouse/GreenExitData.csv", header = TRUE)
gTBseed <- read.csv("~/Desktop/GitHub/TBDCFit/Data/Greenhouse/GreenTBSeed.csv", header = TRUE)
gDCseed <- read.csv("~/Desktop/GitHub/TBDCFit/Data/Greenhouse/GreenDCSeed.csv", header = TRUE)
#gflowers <- read.csv("~/Desktop/GitHub/TBDCFit/Data/Greenhouse/GreenNumFlowers.csv", header = TRUE)
```

# 1. Get seed set per plant

Remove unneeded rows from  pods

```{r}
gpods <- gpods %>%
  select(pid, num.pods.m)
```

Exclude any pods that matured later/had no mature pods

```{r}
gpods <- gpods[gpods$num.pods.m != 0, ]
```


Seed mass per TB pod 

```{r}
gTBseed$mass.per.pod <- gTBseed$Mass..g. / gTBseed$Total.Pods
```

Remove unnecessary columns from TBseed

```{r}
gTBseed <- gTBseed %>%
  select(pid = PID, mass.per.pod)
```

Seed num for DC

```{r}
#1. List of unique PIDs in DCseed

DCpid <- unique(gDCseed$pid)

#2. Make output dataset

gDCseedout <- data.frame(pid = DCpid, 
                        pod.avg = 0)

#3. write the for loop 

for(i in 1:length(DCpid)){
  subset <- gDCseed[gDCseed$pid == DCpid[i], ]
  gDCseedout[i, 2] <- mean(subset$num.m.seeds)
}
```

## 2. Get standardized seed set metric

1. Multiply avg seed set per plant by number of mature pods produced
2. Get median of control group seed set by each plant type
3. Divide each individual by that mean 
4. Combine into one dataset 

### Step 1


```{r}
gDCseedout <- merge(gDCseedout, gpods, by = "pid")
gTBseed <- merge(gTBseed, gpods, by = "pid")

gDCseedout$tot.seed.set <- gDCseedout$pod.avg * gDCseedout$num.pods.m
gTBseed$tot.seed.set <- gTBseed$mass.per.pod * gTBseed$num.pods.m
```


### Step 2

Select correct columns from key

```{r}
gkey <- gkey %>%
  select(pid, type, treatment, column)
```


```{r}
gDCseedout <- merge(gDCseedout, gkey, by = "pid")

gDCseedout <- gDCseedout %>%
  select(pid, type, treatment, column, tot.seed.set)

gDCseedCON <- gDCseedout[gDCseedout$treatment == "CON", ]

gmedianDC <- median(gDCseedCON$tot.seed.set)

```


```{r}
gTBseed <- merge(gTBseed, gkey, by = "pid")

gTBseed <- gTBseed %>%
  select(pid, type, treatment, column, tot.seed.set)

gTBseedCON <- gTBseed[gTBseed$treatment == "CON", ]

gmedianTB <- median(gTBseedCON$tot.seed.set)

```


```{r}
gDCseedout$stand.seed <- gDCseedout$tot.seed.set / gmedianDC

gTBseed$stand.seed <- gTBseed$tot.seed.set / gmedianTB
```

## 3. Combine everything together

```{r}
ggerm <- ggerm %>%
  select(pid, prop.sprouted)

gcomb <- merge(garea, ggerm, by.x = "PID", by.y = "pid")
#comb <- merge(comb, pods, by = "PID")

gcomb <- merge(gcomb, gDCseedout, by.x = c("PID", "treatment", "type"), by.y = c("pid", "treatment", "type"), all.x = TRUE)
gcomb <- merge(gcomb, gTBseed, by.x = c("PID", "treatment", "type"), by.y = c("pid", "treatment", "type"), all.x = TRUE)

gcomb$column <- paste(gcomb$column.x, gcomb$column.y, sep = "")
gcomb$column <- gsub("NA", "", gcomb$column)


gcomb$stand.seed.set <- paste(gcomb$stand.seed.x, gcomb$stand.seed.y, sep = "")
gcomb$stand.seed.set <- gsub("NA", "", gcomb$stand.seed.set)
```


### Calculate fitness: 

```{r}
gcomb$stand.seed.set <- as.numeric(gcomb$stand.seed.set)
gcomb$ln.stand.seed.set <- log(gcomb$stand.seed.set)

gcomb$rel.fitness <- gcomb$prop.sprouted * gcomb$ln.stand.seed.set
```

# 4. Graph!

```{r}
greenfitnessplot <- ggplot(data = gcomb, aes(x = tot.area, y = rel.fitness)) + 
  theme_bw() + 
  geom_smooth(aes(linetype = type), color = "black", method = "lm", alpha = 0.2) + 
  scale_linetype_manual(values = c("dotdash", "solid")) + 
  geom_point(aes(shape = type,  color = treatment)) + 
  scale_color_manual(values = c("black", "#1E88E5", "lime green", "#D81B60")) + 
  scale_shape_manual(values = c(1, 16)) + 
  labs(x = expression(paste("Leaf area consumed ", (cm^{2}))), y = "Relative fitness", color = "Treatment group",
       shape = "Hostplant", linetype = "Hostplant")

greenfitnessplot

```


```{r}
ggsave("~/Desktop/GitHub/TBDCFit/Figures/greenfitnessherb.png", greenfitnessplot, width = 8, height = 5)
```



```{r}
greenseedsetplot <- ggplot(data = gcomb, aes(x = tot.area, y = ln.stand.seed.set)) + 
  theme_bw() + 
  geom_smooth(aes(linetype = type), color = "black", method = "lm", alpha = 0.2) + 
  scale_linetype_manual(values = c("dotdash", "solid")) + 
  geom_point(aes(shape = type,  color = treatment)) + 
  scale_color_manual(values = c("black", "#1E88E5", "lime green", "#D81B60")) + 
  scale_shape_manual(values = c(1, 16)) + 
  labs(x = expression(paste("Leaf area consumed ", (cm^{2}))), y = "Standardized seed set", color = "Treatment group",
       shape = "Hostplant", linetype = "Hostplant")

greenseedsetplot

```

```{r}
greengermplot <- ggplot(data = gcomb, aes(x = tot.area, y = prop.sprouted)) + 
  theme_bw() + 
  geom_smooth(aes(linetype = type), color = "black", method = "lm", alpha = 0.2) + 
  scale_linetype_manual(values = c("dotdash", "solid")) + 
  geom_point(aes(shape = type,  color = treatment)) + 
  scale_color_manual(values = c("black", "#1E88E5", "lime green", "#D81B60")) + 
  scale_shape_manual(values = c(1, 16)) + 
  labs(x = expression(paste("Leaf area consumed ", (cm^{2}))), y = "Proportion germinated", color = "Treatment group",
       shape = "Hostplant", linetype = "Hostplant") +
  ylim(0, 1)

greengermplot

```

# 5. Fitness stats


```{r}
greenfitmod <- lmer(rel.fitness ~ tot.area*type + (1|column), data = gcomb)

summary(greenfitmod)
```


```{r}
greenseedsetmod <- lmer(ln.stand.seed.set ~ tot.area*type + (1|column), data = gcomb)

summary(greenseedsetmod)
```


```{r}
greengermmod <- glmer(prop.sprouted ~ tot.area*type + (1|column), data = gcomb, family = "binomial")

summary(greengermmod)
```


```{r}
greengermmod2 <- glm(prop.sprouted ~ tot.area*type, data = gcomb, family = "binomial")

summary(greengermmod2)
```

