---
title: "Heat map analysis"
output: html_notebook
---

Joel wants me to make a heat map, showing plant condition across the plot and then plant seed production across the plot. This document creates those maps. 


## 0. Load in packages and data

```{r}
library(tidyverse)
library(ggplot2)
```



```{r}
#herb <- read.csv("~/Desktop/GitHub/TBDCFit/Data/HerbivoryCleaned.csv", header = TRUE)
pods <- read.csv("~/Desktop/GitHub/TBDCFit/Data/ExitData.csv", header = TRUE)
TBseed <- read.csv("~/Desktop/GitHub/TBDCFit/Data/TBSeed.csv", header = TRUE)
DCseed <- read.csv("~/Desktop/GitHub/TBDCFit/Data/DCSeed.csv", header = TRUE)
#germ <- read.csv("~/Desktop/GitHub/TBDCFit/Data/GermCollated.csv", header = TRUE)
key <- read.csv("~/Desktop/GitHub/TBDCFit/Data/pidTrtKey.csv", header = TRUE)
census <- read.csv("~/Desktop/GitHub/TBDCFit/Data/CensusAug28.csv", header = TRUE)
```



## 1. Clean the data 

**We want the following things in our dataset: pid, plant type, column, row, condition, and seed set. **

```{r}
key <- key %>%
  select(pid, type, row, column)
```

```{r}
TBseed <- TBseed %>%
  select(pid, pod.avg)
```

```{r}
pods <- pods %>%
  select(PID, condition, num.pod.m)
pods$conditionend <- pods$condition

pods <- pods %>%
  select(PID, conditionend, num.pod.m)
```

```{r}
census <- census %>%
  select(pid, condition)
```


```{r}
#1. List of unique PIDs in DCseed

DCpid <- unique(DCseed$pid)

#2. Make output dataset

DCseedout <- data.frame(pid = DCpid, 
                        pod.avg = 0)

#3. write the for loop 

for(i in 1:length(DCpid)){
  subset <- DCseed[DCseed$pid == DCpid[i], ]
  DCseedout[i, 2] <- mean(subset$num.m.seeds)
}
```

### Remove individuals that we couldn't sample due to mold/error

```{r}
TBseed <- TBseed[TBseed$pid != 23, ]
TBseed <- TBseed[TBseed$pid != 141, ]
```


```{r}
DCseedout <- DCseedout[DCseedout$pid != 78, ]
DCseedout <- DCseedout[DCseedout$pid != 140, ]
```


```{r}
pods <- pods[pods$PID != 23, ]
pods <- pods[pods$PID != 141, ]
pods <- pods[pods$PID != 78, ]
pods <- pods[pods$PID != 140, ]
```


### Combine into one dataset

```{r}
comb <- merge(key, pods, by.x = "pid", by.y = "PID")

combTB <- comb[comb$type == "TB", ]

combDC <- comb[comb$type == "DC", ]

combTB <- merge(combTB, TBseed, by = "pid", all.x = TRUE)
combDC <- merge(combDC, DCseedout, by = "pid", all.x = TRUE)

comb <- rbind(combTB, combDC)

comb$repro <- comb$num.pod.m * comb$pod.avg

comb$repro[is.na(comb$repro)] <- 0

comb$lnrepro <- log(comb$repro + 1)

comb <- merge(comb, census, by = "pid")


comb$column <- gsub("C ", "C", comb$column)

comb$row <- -(comb$row)
```

*Issue with TB plants 9, 25, 27, 59 - no pods but pod masses?? Left in as 0s for now*


##  2. Make the heatmaps

### Middle condition

```{r}
ggplot(data = comb, aes(x = column, y = row, fill = condition)) + 
  theme_bw() + 
  geom_tile() + 
  scale_fill_gradient(low = "#F98B0B", high = "#360E61") + 
  labs(x = "Column of plot", y  = "Row of plot", fill = "Condition of plant")
```

### End  condition

```{r}
ggplot(data = comb, aes(x = column, y = row, fill = conditionend)) + 
  theme_bw() + 
  geom_tile() + 
  scale_fill_gradient(low = "#F98B0B", high = "#360E61") + 
  labs(x = "Column of plot", y  = "Row of plot", fill = "Condition of plant")
```


### Seed set for DC

```{r}
ggplot(data = comb[comb$type == "DC", ], aes(x = column, y = row, fill = lnrepro)) + 
  theme_bw() + 
  geom_tile() + 
  scale_fill_gradient(low = "#76D053", high = "#267C8E") + 
  labs(x = "Column of plot", y  = "Row of plot", fill = "ln(Total seed set)")
```


### Seed set for TB

```{r}
ggplot(data = comb[comb$type == "TB", ], aes(x = column, y = row, fill = lnrepro)) + 
  theme_bw() + 
  geom_tile() + 
  scale_fill_gradient(low = "#76D053", high = "#267C8E") + 
  labs(x = "Column of plot", y  = "Row of plot", fill = "ln(Total seed set)")
```

