---
title: "Herbivory Cleaning and Analysis"
output: html_notebook
---

This document cleans the herbivory dataset to get maximum herbivory data for each plant. 

Steps: 
0. Load packages and the dataset
1. Subset the data for each plant
2. Determine whether the WOWEs were WOWEs or WOWE mongos, and how to count their consumed leaves as such 
3. Determine whether each plant had a caterpillar go to completion, and remove the ones that didn't 
4. Fix the data so we have one value per plant, to graph and analyze for Tyler
5. Remake the graphs and do the analyses

**I decided to do steps 2-4 in Excel, to make a new dataset in an easier fashion than adding row-by-row in R**

# 0. Load in the packages and dataset

```{r}
library(tidyverse)
library(ggplot2)
```

```{r}
herb <- read.csv("~/Desktop/GitHub/TBDCFit/Data/herbivory.csv", header = TRUE)
```

# 1. Subset the data for each plant

```{r}
PIDs <- unique(herb$pid)
for(i in 1:length(PIDs)) {
  subset <- herb[herb$pid == PIDs[[i]], ]
  print(subset)
}
```

# 2-4. Load in the new fixed dataset

```{r}
herbc <- read.csv("~/Desktop/GitHub/TBDCFit/Data/HerbivoryCleaned.csv", header = TRUE)
```

# 5. Remake the graphs and do the analyses

## Complete development only


```{r}
herbcomp <- herbc[herbc$dev.complete == "yes", ]
herbcomp <- herbcomp[herbcomp$treatment != "CON", ]
```

### Stats - leaf number differ by treatment?

```{r}
leafnumDC <- lm(num.leaf ~ treatment, data = herbcomp[herbcomp$type == "DC", ])

summary(leafnumDC)
```


```{r}
leafnumTB <- lm(num.leaf ~ treatment, data = herbcomp[herbcomp$type == "TB", ])

summary(leafnumTB)
```

In both DC and TB, WEs eat less than WOWEs or WANDs, but the other two are indistinguishable. 

### Graphs - leaf num by mature pod num 

```{r}
poddata <- read.csv("~/Desktop/GitHub/TBDCFit/Data/ExitData.csv", header = TRUE)
```

Add pod data to leaf dataset

```{r}
comb <- merge(herbc, poddata, by.x = "pid", by.y = "PID")
```

```{r}
ggplot(comb[comb$treatment != "CON", ], aes(x = num.leaf, y = num.pod.m, color = treatment)) + 
  theme_bw() + 
  facet_wrap(facets = "type") + 
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE)
```


```{r}
ggplot(comb[comb$treatment != "CON", ], aes(x = num.leaf, y = num.pod.m + num.pod.im, color = treatment)) + 
  theme_bw() + 
  facet_wrap(facets = "type") + 
  geom_point() + 
  geom_smooth(method = "lm", se = FALSE)
```
