---
title: "figures and Stats for Honors Thesis"
output: html_notebook
---

This notebook will make the figures and run the stats for Tyler's Honors Thesis. 

## 0. Load libraries and data

```{r}
library(tidyverse)
library(ggplot2)
library(lmerTest)
```

```{r}
herb <- read.csv("~/Desktop/GitHub/TBDCFit/Data/HerbivoryCleaned.csv", header = TRUE)
pods <- read.csv("~/Desktop/GitHub/TBDCFit/Data/ExitData.csv", header = TRUE)
TBseed <- read.csv("~/Desktop/GitHub/TBDCFit/Data/TBSeed.csv", header = TRUE)
DCseed <- read.csv("~/Desktop/GitHub/TBDCFit/Data/DCSeed.csv", header = TRUE)
```

## 1. Clean the data

Remove the individuals that had mature pods that we couldn't measure due to damage/mold

```{r}
TBseed <- TBseed[TBseed$pid != 23, ]
TBseed <- TBseed[TBseed$pid != 141, ]
```

```{r}
pods <- pods[pods$PID != 23, ]
pods <- pods[pods$PID != 141, ]
```

Remove unneeded rows from TBseed and pods

```{r}
TBseed <- TBseed %>%
  select(pid, mature, kept, pod.avg)
```

```{r}
pods <- pods %>%
  select(PID, num.pod.m)
```

### Write a for loop to get avg seed number per pod for DC

```{r}
#1. List of unique PIDs in DCseed

DCpid <- unique(DCseed$pid)

#2. Make output dataset

DCseedout <- data.frame(pid = DCpid, 
                        pod.avg = 0)

#3. write the for loop 

for(i in 1:length(DCpid)){
  subset <- DCseed[DCseed$pid == DCpid[i], ]
  DCseedout[i, 2] <- mean(subset$num.m.seeds)
}
```

Merge datasets into master dataset

```{r}
comb <- merge(herb, pods, by.x = "pid", by.y = "PID")

combTB <- comb[comb$type == "TB", ]

combDC <- comb[comb$type == "DC", ]

combTB <- merge(combTB, TBseed, by = "pid", all.x = TRUE)
combDC <- merge(combDC, DCseedout, by = "pid", all.x = TRUE)
```

### Remove DC where we couldn't find pods / pods rotten

```{r}
combDC <- combDC[combDC$pid != 78, ]
combDC <- combDC[combDC$pid != 140, ]
```



Get seed resources per pod calculation

Tobacco: mass of each pod
DC: num seeds per pod (avg)

Get total reproductive output

Tobacco: avg mass * num mature pods
DC: avg num seeds * num mature pods

```{r}
combTB$repro <- combTB$num.pod.m * combTB$pod.avg
combDC$repro <- combDC$num.pod.m * combDC$pod.avg
```

Get zeros in reproductive output with no mature pods

```{r}
combTB$repro[is.na(combTB$repro)] <- 0
combDC$repro[is.na(combDC$repro)] <- 0
#comb <- mutate_at(comb$repro, ~replace(., is.na(.), 0))
```

Add column to the datatable

```{r}
key <- read.csv("~/Desktop/GitHub/TBDCFit/Data/pidTrtKey.csv", header = TRUE)

key <- key %>%
  select(pid, column)

combTB <- merge(combTB, key, by = "pid")
combDC <- merge(combDC, key, by = "pid")
```

Add log-scaled repro output

```{r}
combTB$logrepro <- log(combTB$repro + 1)
combDC$logrepro <- log(combDC$repro + 1)
```



## 2. Make figures!!

### Fig. 1: Methods Figure

### Fig. 2: Number of leaves consumed across treatment groups

Only individuals that completed development

```{r}
fig2DC <- ggplot(data = combDC[combDC$dev.complete == "yes", ], 
                 aes(treatment, num.leaf)) + 
  theme_bw() + 
  geom_boxplot() + 
  geom_jitter(width = 0.1, alpha = 0.5) + 
  labs(x = "Treatment Group", y = "Number of leaves consumed", title = "A) Devil's Claw")

fig2DC
ggsave("~/Desktop/GitHub/TBDCFit/Figures/fig2DC.png", plot = fig2DC, width = 8, height = 5)
```


```{r}
fig2TB <- ggplot(data = combTB[combTB$dev.complete == "yes", ], 
                 aes(treatment, num.leaf)) + 
  theme_bw() + 
  geom_boxplot() + 
  geom_jitter(width = 0.1, alpha = 0.5) + 
  labs(x = "Treatment Group", y = "Number of leaves consumed", title = "B) Tobacco")

fig2TB
ggsave("~/Desktop/GitHub/TBDCFit/Figures/fig2TB.png", plot = fig2TB, width = 8, height = 5)
```

### Fig. 3: total realized reproductive output vs. herbivory

```{r}
fig3DCln <- ggplot(data = combDC, 
                 aes(x = num.leaf, y = logrepro, color = treatment)) + 
  theme_bw() + 
  geom_point() + 
  scale_color_manual(values = c("#1E88E5", "lime green", "orange", "#D81B60")) + 
  labs(x = "Number of leaves consumed", y = "Total reproductive output (ln(number of seeds))", title = "A) Devil's claw", 
       color = "Treatment")

fig3DCln

ggsave("~/Desktop/GitHub/TBDCFit/Figures/fig3DCln.png", plot = fig3DCln, width = 8, height = 5)
```


```{r}
fig3TBln <- ggplot(data = combTB, 
                 aes(x = num.leaf, y = logrepro, color = treatment)) + 
  theme_bw() + 
  geom_point() + 
  scale_color_manual(values = c("#1E88E5", "lime green", "orange", "#D81B60")) + 
  labs(x = "Number of leaves consumed", y = "Total reproductive output (ln(mg of seeds))", title = "B) Tobacco", 
       color = "Treatment")

fig3TBln
ggsave("~/Desktop/GitHub/TBDCFit/Figures/fig3TBln.png", plot = fig3TBln, width = 8, height = 5)
```



## Statistics: 

### ANOVA for Fig. 2

```{r}
leafDC <- lm(num.leaf ~ treatment, 
             data = combDC[combDC$treatment != "CON" & combDC$dev.complete == "yes", ])

summary(leafDC)
anova(leafDC)
```


```{r}
leafTB <- lm(num.leaf ~ treatment, 
             data = combTB[combTB$treatment != "CON" & combTB$dev.complete == "yes", ])

summary(leafTB)
anova(leafTB)
```

### LM for Fig. 3 new

### Checking some stuff

```{r}
columnTB <- lm(repro ~ column, data = combTB)
#take residuals of this model and have it be the response variable 

anova(columnTB)

combTB$residuals <- columnTB$residuals

residTB <- lm(residuals ~ num.leaf, data = combTB)
trtTB <- lm(residuals ~ treatment, data = combTB)

anova(residTB)

```

```{r}
fieldTB <- ggplot(combTB, aes(x = column, y = repro)) + 
  theme_bw() + 
  geom_boxplot() + 
  geom_jitter(width = 0.1) + 
  ylim(0, 25000) + 
  labs(x = "Column in Field Plot", y = "Total Reproductive Output (mass of seedpods (mg))", title = "B) Tobacco")

ggsave("~/Desktop/GitHub/TBDCFit/Figures/SuppFigTB.png", fieldTB, width = 8, height = 5)
```


```{r}
columnDC <- lm(repro ~ column, data = combDC)
#take residuals of this model and have it be the response variable 

anova(columnDC)

combDC$residuals <- columnDC$residuals

residDC <- lm(residuals ~ num.leaf, data = combDC)

anova(residDC)

```


```{r}
fieldDC <- ggplot(combDC, aes(x = column, y = repro)) + 
  theme_bw() + 
  geom_boxplot() + 
  geom_jitter(width = 0.1) + 
  ylim(0, 1000) + 
  labs(x = "Column of Field Plot", y = "Total Reproductive Output (number of seeds)", title = "A) Devil's Claw")

ggsave("~/Desktop/GitHub/TBDCFit/Figures/SuppFigDC.png", fieldDC, width = 8, height = 5)
```

