---
title: "Leaf Area Analysis 2022"
output: html_notebook
---

This notebook gives the correct leaf area consumed calculations used on both the greenhouse and field data. 

Roadmap: 

0. Load in the data and packages
1. Make the output file 
2. Make the giant for loop
3. Graph output for checking accuracy


# 0. Load in the packages and data

```{r}
library(ggplot2)
library(tidyverse)
library(sjmisc)
```

```{r}
herbfield <- read.csv("~/Desktop/GitHub/TBDCFit/Data/HerbCleaned2022.csv", header = TRUE)
herbgreen <- read.csv("~/Desktop/GitHub/TBDCFit/Data/Greenhouse/GreenHerbAug23.csv", header = TRUE)

keyfield <- read.csv("~/Desktop/GitHub/TBDCFit/Data/pidTrtKey.csv", header = TRUE)
keygreen <- read.csv("~/Desktop/GitHub/TBDCFit/Data/Greenhouse/GreenPIDTrtKey.csv", header = TRUE)
```

# 1. Make the output file

```{r}
addedfield <- data.frame(date = "9/1", 
                         cid = NA,
                         pid = keyfield$pid, 
                         num.leaf = NA, 
                         position = NA, 
                         exit = NA)

herbfield <- rbind(herbfield, addedfield)

outputfield <- data.frame(PID = unique(herbfield$pid), 
                          tot.area = 0)

outputfield <- outputfield %>%
  arrange(PID)
```

```{r}
addedgreen <- data.frame(date = "8/20", 
                         pid = keygreen$pid, 
                         num.leaf = NA, 
                         position = NA, 
                         exit = NA, 
                         notes = NA)

herbgreen <- rbind(herbgreen, addedgreen)
#herbgreen <- rbind(herbgreen, addedgreen)

outputgreen <- data.frame(PID = unique(herbgreen$pid), 
                          tot.area = 0)

outputgreen <- outputgreen %>%
  arrange(PID)
```

Trying it with the greenhouse in the right order

```{r}
herbgreen$cid <- NA
herbgreen <- herbgreen %>%
  select(date, cid, pid, num.leaf, position, exit)
```


# 2. Make the heinous for loop

0. Subset by PID and order by leaf num
1. Distinguish between end (NA) and non-end (Non-NA)
2. Distinguish between higher leaf num and not 
3. Distinguish between DC and TB (even/odd PID)
4. Add appropriate leaf area to total running count if leaf num higher, otherwise add 0
5. Input into output dataframe


THIS WORKS NOW

```{r}
leafarea <- function(dataframe, output){
  
  for(i in (1:length(output$PID))){
    k <- output[i, 1]
    #print(k)
    subset <- dataframe[dataframe$pid == k, ]
    #print(subset$pid)
    subset <- subset %>%
      arrange(num.leaf)
    value <- 0
  
  for(j in 1:length(subset$pid)){
    if(is.na(subset[j+1, 4]) == FALSE){
      if(subset[j+1, 4] > subset[j, 4]){
        if(subset[j+1, 4] == (subset[j, 4] + 1)){
          if(is_odd(subset[j, 3]) == TRUE){
            if(subset[j, 5] == "T"){
              value <- value + 50
              } else 
                if(subset[j, 5] == "M"){
                  value <- value + 200
                } else
                  if(subset[j, 5] == "B"){
                    value <- value + 250
                  }
            } else if(is_even(subset[j, 3]) == TRUE){
            if(subset[j, 5] == "T"){
              value <- value + 50
              } else 
                if(subset[j, 5] == "M"){
                  value <- value + 125
                } else
                  if(subset[j, 5] == "B"){
                    value <- value + 150
                  }
          }
        } else if(subset[j+1, 4] > subset[j, 4] + 1){
          if(is_odd(subset[j, 3]) == TRUE){
            if(subset[j, 5] == "T"){
              value <- value + (50 * (subset[j+1, 4] - subset[j, 4]))
              } else 
                if(subset[j, 5] == "M"){
                  value <- value + (200 * (subset[j+1, 4] - subset[j, 4]))
                } else
                  if(subset[j, 5] == "B"){
                    value <- value + (250 * (subset[j+1, 4] - subset[j, 4]))
                  }
          } else if(is_even(subset[j, 3]) == TRUE){
            if(subset[j, 5] == "T"){
              value <- value + (50 * (subset[j+1, 4] - subset[j, 4]))
              } else 
                if(subset[j, 5] == "M"){
                  value <- value + (125 * (subset[j+1, 4] - subset[j, 4]))
                } else
                  if(subset[j, 5] == "B"){
                    value <- value + (150 * (subset[j+1, 4] - subset[j, 4]))
                  }
          }
        }
      } else if(subset[j+1, 4] <= subset[j, 4]){
        value <- value + 0
      }
    } else if(is.na(subset[j+1, 4]) == TRUE){
      value <- value
    }
  }
  output[i, 2] <- value
}
  output <- output
  return(output)
}
```


```{r}
outputfield <- leafarea(dataframe = herbfield, output = outputfield)
```


```{r}
outputgreen <- leafarea(dataframe = herbgreen, output = outputgreen)
```


this looks great! Graph to test output: 

# 3. Graph (after adding treatment)

```{r}
keyfield <- keyfield %>%
  select(pid, type, treatment)

keygreen <- keygreen %>%
  select(pid, type, treatment)
```

```{r}
outputfield <- merge(outputfield, keyfield, by.x = "PID", by.y = "pid")

outputgreen <- merge(outputgreen, keygreen, by.x = "PID", by.y = "pid")
```

```{r}
ggplot(outputfield, aes(x = treatment, y = tot.area, color = type)) + 
  theme_bw() + 
  geom_boxplot() + 
  labs(x = "Treatment", y = "Total leaf area consumed (cm2)", color = "Plant Type")
```



```{r}
ggplot(outputgreen, aes(x = treatment, y = tot.area, color = type)) + 
  theme_bw() + 
  geom_boxplot() + 
  labs(x = "Treatment", y = "Total leaf area consumed (cm2)", color = "Plant Type")
```

# 4. Export new leaf area files to use


```{r}
write.csv(x = outputfield, file = "~/Desktop/GitHub/TBDCFit/Data/FieldLeafArea.csv", row.names = FALSE)
write.csv(x = outputgreen, file = "~/Desktop/GitHub/TBDCFit/Data/Greenhouse/GreenLeafArea.csv", row.names = FALSE)
```

