---
title: "Field Summary Statistics"
output: html_notebook
---

This script will run linear models on each variable from the summary table and assess the contributions of treatment and/or hostplant to that variable's variation. 


Roadmap: 

0. Load in the data
1. Run binomial regressions for each "percentage" statistic
  a. Remake "binary" columns for each stat that we made in SummaryTable.Rmd
  b. Run the linear model with treatment, hostplant, and their interaction as predictors and column as a random effect
  c. Run an ANOVA and input the F-value and p-value into the first table on Google Drive
2. Run linear regression on total leaf area consumed
  a. treatment, hostplant, and their interaction as predictors and column as a random effect
  b. Run an ANOVA and input the F-value and p-value into the first table on Google Drive
3. Run linear regressions for each "number" statistic
  a. Run the linear model with treatment as a predictor and column as a random effect separately for each hostplant
  b. Run an ANOVA and input the F-value and p-value into the first table on Google Drive
  


# 0. Load in the data

```{r}
library(tidyverse)
library(lmerTest)
library(car)
```



```{r}
farea <- read.csv("~/Desktop/GitHub/TBDCFit/Data/FieldLeafArea.csv", header = TRUE)
fgerm <- read.csv("~/Desktop/GitHub/TBDCFit/Data/GermCollated.csv", header = TRUE)
fkey <- read.csv("~/Desktop/GitHub/TBDCFit/Data/pidTrtKey.csv", header = TRUE)
fpods <- read.csv("~/Desktop/GitHub/TBDCFit/Data/ExitData.csv", header = TRUE)
fTBseed <- read.csv("~/Desktop/GitHub/TBDCFit/Data/TBSeedCorrect.csv", header = TRUE)
fDCseed <- read.csv("~/Desktop/GitHub/TBDCFit/Data/DCSeed.csv", header = TRUE)
fflowers <- read.csv("~/Desktop/GitHub/TBDCFit/Data/FieldNumFlowers.csv", header = TRUE)
```

# 1. Proportion metrics

## Proportion of plants that flowered

```{r}
fkey <- fkey %>%
  select(pid, type, treatment, column)

fflowers <- merge(fflowers, fkey, by = "pid")

fflowers$binary <- 0
```

for loop for binary assignment 

```{r}
for(i in 1:length(fflowers$pid)){
  if(fflowers[i, 2] > 0){
    fflowers[i, 6] <- 1
  } else if(fflowers[i, 2] <= 0){
    fflowers[i, 6] <- 0
  }
}

```

Run the linear model 

```{r}
fpropflowermod <- glm(binary ~ treatment*type, data = fflowers, family = "binomial")

summary(fpropflowermod)
```

Run the anova

```{r}
anova(fpropflowermod, test = "Chisq")
```


Run Anova from "car" package

```{r}
Anova(fpropflowermod, type = 3)
```



