---
title: "Summary Table Code"
output: html_notebook
---

This script will make the summary table to include in the manuscript. 

Contents: 

1. % plants with flowers
  - extract which plants had any flowers from final flowering datasheet
2. # flowers / plant
  - take the mean of those with flowers by trt and type
3. % plants with mature pods
  - extract which plants had any pods from final pod datasheet
4. # pods / plant
  - take the mean of those with mature pods by trt and type
5. #/mass of seeds / pod
  - take the mean of those by trt and type
6. % seeds germinated
  - take the mean of those who we germinated from by trt and type
7. area of leaves consumed
  - take the mean from final herbivory datasheet

Roadmap: 

0. Load in packages and datasets
1. Make output file
2. Go through 1-6 each in order, adding to an output datafile. 
3. Export output datafile as a csv. 


# 0. Load in our packages and datasets 

```{r}
library(tidyverse)
library(Rmisc)
library(ggplot2)
```

## FIELD: 

```{r}
farea <- read.csv("~/Desktop/GitHub/TBDCFit/Data/FieldLeafArea.csv", header = TRUE)
fgerm <- read.csv("~/Desktop/GitHub/TBDCFit/Data/GermCollated.csv", header = TRUE)
fkey <- read.csv("~/Desktop/GitHub/TBDCFit/Data/pidTrtKey.csv", header = TRUE)
fpods <- read.csv("~/Desktop/GitHub/TBDCFit/Data/ExitData.csv", header = TRUE)
fTBseed <- read.csv("~/Desktop/GitHub/TBDCFit/Data/TBSeedCorrect.csv", header = TRUE)
fDCseed <- read.csv("~/Desktop/GitHub/TBDCFit/Data/DCSeed.csv", header = TRUE)
fflowers <- read.csv("~/Desktop/GitHub/TBDCFit/Data/FieldNumFlowers.csv", header = TRUE)
```


# 1. Output file

```{r}
metrics <- c("percentflowers", "numflowers", "percentpods", "numpods", "numseeds", "percentgerm", "leafarea")

foutput <- data.frame(metric = metrics, 
                     N = 0, 
                     DCCONmean = 0, 
                     DCCONse = 0, 
                     DCWANDmean = 0, 
                     DCWANDse = 0,
                     DCWEmean = 0, 
                     DCWEse = 0,
                     DCWOWEmean = 0, 
                     DCWOWEse = 0,
                     TBCONmean = 0, 
                     TBCONse = 0, 
                     TBWANDmean = 0, 
                     TBWANDse = 0,
                     TBWEmean = 0, 
                     TBWEse = 0,
                     TBWOWEmean = 0, 
                     TBWOWEse = 0)
```


# 2. Go through each metric

## 1. Percent flowers

Datafile: output of for loop (fflowers), key (fkey)
Approach: Create binary column, subset by Trt+Type, take number of 1s over total number


get requisite columns in dataframe

```{r}
fkey <- fkey %>%
  select(pid, type, treatment)

fflowers <- merge(fflowers, fkey, by = "pid")

fflowers$binary <- 0

fflowers$composite <- paste(fflowers$type, fflowers$treatment, sep = " ")
```

for loop for binary assignment 

```{r}
for(i in 1:length(fflowers$pid)){
  if(fflowers[i, 2] > 0){
    fflowers[i, 5] <- 1
  } else if(fflowers[i, 2] <= 0){
    fflowers[i, 5] <- 0
  }
}

```

for loop for subsetting and getting percentages

```{r}
fflowperc <- data.frame(composite = unique(fflowers$composite), 
                        perc = 0)

fflowperc <- fflowperc[order(fflowperc$composite), ]

uniquecomp <- fflowperc$composite

for(i in 1:length(uniquecomp)){
  k <- uniquecomp[[i]]
  subset <- fflowers[fflowers$composite == k, ]
  #print(subset)
  fflowperc[fflowperc$composite == k, 2] <- (sum(subset$binary)) / (length(subset$binary))
}
```

Add to output table

```{r}
foutput[1, 2] <- 168

foutput[1, 3] <- fflowperc[1, 2]
foutput[1, 5] <- fflowperc[2, 2]
foutput[1, 7] <- fflowperc[3, 2]
foutput[1, 9] <- fflowperc[4, 2]
foutput[1, 11] <- fflowperc[5, 2]
foutput[1, 13] <- fflowperc[6, 2]
foutput[1, 15] <- fflowperc[7, 2]
foutput[1, 17] <- fflowperc[8, 2]
```

## 2. Number of flowers per plant

Data: output of total flowers (fflowers)
Approach: subset by those that flowered, then summarySE 

```{r}
fflowersyes <- fflowers[fflowers$binary == 1, ]

ftotflow <- summarySE(data = fflowersyes,
                      measurevar = "tot.flowers", 
                      groupvars = "composite")
```

Add to final output 

```{r}
foutput[2, 2] <- sum(ftotflow$N)

foutput[2, 3] <- ftotflow[1, 3]
foutput[2, 4] <- ftotflow[1, 5]
foutput[2, 5] <- ftotflow[2, 3]
foutput[2, 6] <- ftotflow[2, 5]
foutput[2, 7] <- ftotflow[3, 3]
foutput[2, 8] <- ftotflow[3, 5]
foutput[2, 9] <- ftotflow[4, 3]
foutput[2, 10] <- ftotflow[4, 5]
foutput[2, 11] <- ftotflow[5, 3]
foutput[2, 12] <- ftotflow[5, 5]
foutput[2, 13] <- ftotflow[6, 3]
foutput[2, 14] <- ftotflow[6, 5]
foutput[2, 15] <- ftotflow[7, 3]
foutput[2, 16] <- ftotflow[7, 5]
foutput[2, 17] <- ftotflow[8, 3]
foutput[2, 18] <- ftotflow[8, 5]

```

## 3. Percent with mature pods

Data: pods datasheets (fpods) + key (fkey)
Approach: get rid of misc columns, create binary, calculate percentage 

```{r}
fpods <- fpods %>%
  select(PID, num.pod.m)

fpods <- merge(fpods, fkey, by.x = "PID", by.y = "pid")

fpods$binary <- 0

fpods$composite <- paste(fpods$type, fpods$treatment, sep = " ")

fpods[24, 2] <- 0 #plant pid = 30 was totally unfound, had no pods

```

```{r}
for(i in 1:length(fpods$PID)){
  if(fpods[i, 2] > 0){
    fpods[i, 5] <- 1
  } else if(fpods[i, 2] <= 0){
    fpods[i, 5] <- 0
  }
}

```

for loop for getting pod counts


```{r}
fpodperc <- data.frame(composite = unique(fpods$composite), 
                        perc = 0)

fpodperc <- fpodperc[order(fpodperc$composite), ]

for(i in 1:length(uniquecomp)){
  k <- uniquecomp[[i]]
  subset <- fpods[fpods$composite == k, ]
  #print(subset)
  fpodperc[fpodperc$composite == k, 2] <- (sum(subset$binary)) / (length(subset$binary))
}
```

put in output table


```{r}
foutput[3, 2] <- 168

foutput[3, 3] <- fpodperc[1, 2]
foutput[3, 5] <- fpodperc[2, 2]
foutput[3, 7] <- fpodperc[3, 2]
foutput[3, 9] <- fpodperc[4, 2]
foutput[3, 11] <- fpodperc[5, 2]
foutput[3, 13] <- fpodperc[6, 2]
foutput[3, 15] <- fpodperc[7, 2]
foutput[3, 17] <- fpodperc[8, 2]
```

## 4. Number of pods per plant

Data: output of total pods (fpods)
Approach: subset by those that had mature pods, then summarySE 

```{r}
fpodsyes <- fpods[fpods$binary == 1, ]

ftotpod <- summarySE(data = fpodsyes,
                      measurevar = "num.pod.m", 
                      groupvars = "composite")
```

```{r}
foutput[4, 2] <- sum(ftotpod$N)

foutput[4, 3] <- ftotpod[1, 3]
foutput[4, 4] <- ftotpod[1, 5]
foutput[4, 5] <- ftotpod[2, 3]
foutput[4, 6] <- ftotpod[2, 5]
foutput[4, 7] <- ftotpod[3, 3]
foutput[4, 8] <- ftotpod[3, 5]
foutput[4, 9] <- ftotpod[4, 3]
foutput[4, 10] <- ftotpod[4, 5]
foutput[4, 11] <- ftotpod[5, 3]
foutput[4, 12] <- ftotpod[5, 5]
foutput[4, 13] <- ftotpod[6, 3]
foutput[4, 14] <- ftotpod[6, 5]
foutput[4, 15] <- ftotpod[7, 3]
foutput[4, 16] <- ftotpod[7, 5]
foutput[4, 17] <- ftotpod[8, 3]
foutput[4, 18] <- ftotpod[8, 5]

```

## 5. Amount of seeds per pod - COME BACK TO THIS

Data: fTBseed, fDCseed, fkey
Approach: Exclude those without pods or that we couldn't measure, use fitness code to get average seed mass/number per plant, then use summarySE to get by treatment group

**Take seed pod mass off of each individual, then average**

Make a binary column for holes in TB pods

```{r}
fTBseed$binary <- 0
```

```{r}
for(i in 1:length(fTBseed$PID)){
  if(fTBseed[i, 3] > 0){
    fTBseed[i, 5] <- 1
  } else if(fTBseed[i, 3] <= 0){
    fTBseed[i, 5] <- 0
  }
}

```

Seed mass per TB pod 

```{r}
fTBseed$mass.per.pod <- fTBseed$Mass..g. / fTBseed$Total.Pods
```

Remove unnecessary columns fromm TBseed

```{r}
fTBseed <- fTBseed %>%
  select(pid = PID, binary = binary, per.pod = mass.per.pod)
```


### Write a for loop to get avg seed number per pod for DC

```{r}
#1. List of unique PIDs in DCseed

fDCpid <- unique(fDCseed$pid)

#2. Make output dataset

fDCseedout <- data.frame(pid = fDCpid, 
                        pod.avg = 0)

#3. write the for loop 

for(i in 1:length(fDCpid)){
  subset <- fDCseed[fDCseed$pid == fDCpid[i], ]
  fDCseedout[i, 2] <- mean(subset$num.m.seeds)
}
```

**Combine datafiles**

```{r}
fDCseedout$binary <- 0 #just adding in because none hadd spodoptera damage

fDCseedout <- fDCseedout %>%
  select(pid, binary, per.pod = pod.avg)
```

```{r}
fperpod <- rbind(fTBseed, fDCseedout)
```


**Add in treatment group**

```{r}
fperpod <- merge(fperpod, fkey, by = "pid")
fperpod$composite <- paste(fperpod$type, fperpod$treatment, sep = " ")
```

**summarySE**

```{r}
fperpodsum <- summarySE(data = fperpod, 
                        measurevar = "per.pod", 
                        groupvars = "composite")
```

**Input into table**

```{r}
foutput[5, 2] <- sum(fperpodsum$N)

foutput[5, 3] <- fperpodsum[1, 3]
foutput[5, 4] <- fperpodsum[1, 5]
foutput[5, 5] <- fperpodsum[2, 3]
foutput[5, 6] <- fperpodsum[2, 5]
foutput[5, 7] <- fperpodsum[3, 3]
foutput[5, 8] <- fperpodsum[3, 5]
foutput[5, 9] <- fperpodsum[4, 3]
foutput[5, 10] <- fperpodsum[4, 5]
foutput[5, 11] <- fperpodsum[5, 3]
foutput[5, 12] <- fperpodsum[5, 5]
foutput[5, 13] <- fperpodsum[6, 3]
foutput[5, 14] <- fperpodsum[6, 5]
foutput[5, 15] <- fperpodsum[7, 3]
foutput[5, 16] <- fperpodsum[7, 5]
foutput[5, 17] <- fperpodsum[8, 3]
foutput[5, 18] <- fperpodsum[8, 5]
```


## 6. Percent germination 

Data: fgerm, fkey
Approach: summarySE

```{r}
fgerm <- merge(fgerm, fkey, by = "pid")

fgerm$composite <- paste(fgerm$type, fgerm$treatment, sep = " ")
```


```{r}
fgermperc <- summarySE(data = fgerm, 
                       measurevar = "prop.sprouted", 
                       groupvars = "composite")


```

Input into summary table

```{r}
foutput[6, 2] <- sum(fgermperc$N)

foutput[6, 3] <- fgermperc[1, 3]
foutput[6, 4] <- fgermperc[1, 5]
foutput[6, 5] <- fgermperc[2, 3]
foutput[6, 6] <- fgermperc[2, 5]
foutput[6, 7] <- fgermperc[3, 3]
foutput[6, 8] <- fgermperc[3, 5]
foutput[6, 9] <- fgermperc[4, 3]
foutput[6, 10] <- fgermperc[4, 5]
foutput[6, 11] <- fgermperc[5, 3]
foutput[6, 12] <- fgermperc[5, 5]
foutput[6, 13] <- fgermperc[6, 3]
foutput[6, 14] <- fgermperc[6, 5]
foutput[6, 15] <- fgermperc[7, 3]
foutput[6, 16] <- fgermperc[7, 5]
foutput[6, 17] <- fgermperc[8, 3]
foutput[6, 18] <- fgermperc[8, 5]
```

## 7. Leaf Area
Data: farea
Approach: summarySE

```{r}
farea$composite <- paste(farea$type, farea$treatment, sep = " ")
```


```{r}
ftotarea <- summarySE(data = farea, 
                       measurevar = "tot.area", 
                       groupvars = "composite")


```

Input into summary table

```{r}
foutput[7, 2] <- 168

foutput[7, 3] <- ftotarea[1, 3]
foutput[7, 4] <- ftotarea[1, 5]
foutput[7, 5] <- ftotarea[2, 3]
foutput[7, 6] <- ftotarea[2, 5]
foutput[7, 7] <- ftotarea[3, 3]
foutput[7, 8] <- ftotarea[3, 5]
foutput[7, 9] <- ftotarea[4, 3]
foutput[7, 10] <- ftotarea[4, 5]
foutput[7, 11] <- ftotarea[5, 3]
foutput[7, 12] <- ftotarea[5, 5]
foutput[7, 13] <- ftotarea[6, 3]
foutput[7, 14] <- ftotarea[6, 5]
foutput[7, 15] <- ftotarea[7, 3]
foutput[7, 16] <- ftotarea[7, 5]
foutput[7, 17] <- ftotarea[8, 3]
foutput[7, 18] <- ftotarea[8, 5]
```

```{r}
write.csv(x = foutput, file = "~/Desktop/GitHub/TBDCFit/Data/FieldSummaryTable.csv", row.names = FALSE)
```


