---
title: "Reduced Dataset Analyses"
output: html_notebook
---

After discussing with my committee on 3/24/22, they suggested only analyzing the plants from columns of "good" quality, and removing the first few columns from the dataset. After discussion with Tyler, we agreed to exclude columns A-F and reanalyze all of the data to observe what trends emerged. 


## 0. Load libraries and data

```{r}
library(tidyverse)
library(ggplot2)
library(lmerTest)
library(lme4)
```


```{r}
herb <- read.csv("~/Desktop/GitHub/TBDCFit/Data/HerbivoryCleaned.csv", header = TRUE)
pods <- read.csv("~/Desktop/GitHub/TBDCFit/Data/ExitData.csv", header = TRUE)
TBseed <- read.csv("~/Desktop/GitHub/TBDCFit/Data/TBSeed.csv", header = TRUE)
DCseed <- read.csv("~/Desktop/GitHub/TBDCFit/Data/DCSeed.csv", header = TRUE)
germ <- read.csv("~/Desktop/GitHub/TBDCFit/Data/GermCollated.csv", header = TRUE)
```


## 1. Clean the data

Remove the individuals that had mature pods that we couldn't measure due to damage/mold

```{r}
TBseed <- TBseed[TBseed$pid != 23, ]
TBseed <- TBseed[TBseed$pid != 141, ]
```

```{r}
pods <- pods[pods$PID != 23, ]
pods <- pods[pods$PID != 141, ]
```

Remove unneeded rows from TBseed and pods

```{r}
TBseed <- TBseed %>%
  select(pid, mature, kept, pod.avg)
```

```{r}
pods <- pods %>%
  select(PID, num.pod.m)
```

### Write a for loop to get avg seed number per pod for DC

```{r}
#1. List of unique PIDs in DCseed

DCpid <- unique(DCseed$pid)

#2. Make output dataset

DCseedout <- data.frame(pid = DCpid, 
                        pod.avg = 0)

#3. write the for loop 

for(i in 1:length(DCpid)){
  subset <- DCseed[DCseed$pid == DCpid[i], ]
  DCseedout[i, 2] <- mean(subset$num.m.seeds)
}
```

Merge datasets into master dataset

```{r}
comb <- merge(herb, pods, by.x = "pid", by.y = "PID")

combTB <- comb[comb$type == "TB", ]

combDC <- comb[comb$type == "DC", ]

combTB <- merge(combTB, TBseed, by = "pid", all.x = TRUE)
combDC <- merge(combDC, DCseedout, by = "pid", all.x = TRUE)
```

### Remove DC where we couldn't find pods / pods rotten

```{r}
combDC <- combDC[combDC$pid != 78, ]
combDC <- combDC[combDC$pid != 140, ]
```



Get seed resources per pod calculation

Tobacco: mass of each pod
DC: num seeds per pod (avg)

Get total reproductive output

Tobacco: avg mass * num mature pods
DC: avg num seeds * num mature pods

```{r}
combTB$repro <- combTB$num.pod.m * combTB$pod.avg
combDC$repro <- combDC$num.pod.m * combDC$pod.avg
```

Get zeros in reproductive output with no mature pods

```{r}
combTB$repro[is.na(combTB$repro)] <- 0
combDC$repro[is.na(combDC$repro)] <- 0
#comb <- mutate_at(comb$repro, ~replace(., is.na(.), 0))
```

### Add column to the datatable

```{r}
key <- read.csv("~/Desktop/GitHub/TBDCFit/Data/pidTrtKey.csv", header = TRUE)

key <- key %>%
  select(pid, column)

combTB <- merge(combTB, key, by = "pid")
combDC <- merge(combDC, key, by = "pid")
```

### Add log-scaled repro output

```{r}
combTB$logrepro <- log(combTB$repro + 1)
combDC$logrepro <- log(combDC$repro + 1)
```

### Remove columns A-F from both datasets

```{r}
combTB2 <- combTB[!(combTB$column == "A" | combTB$column == "B" | combTB$column == "C" | combTB$column == "D" | 
                   combTB$column == "E" | combTB$column == "F" | combTB$column == "C "), ]

combDC2 <- combDC[!(combDC$column == "A" | combDC$column == "B" | combDC$column == "C" | combDC$column == "D" | 
                   combDC$column == "E" | combDC$column == "F"), ]
```

### Add germination data

```{r}
germ <- germ %>%
  select(pid, flat, num.seeds, prop.sprouted)

combTBgerm <- merge(combTB2, germ, by = "pid")
combDCgerm <- merge(combDC2, germ, by = "pid")
```

## 2. Run analyses 

### Leaf number consumed across treatment groups - SIGNIFICANT

```{r}
leafDC <- lm(num.leaf ~ treatment, 
             data = combDC2[combDC2$treatment != "CON" & combDC2$dev.complete == "yes", ])

summary(leafDC)
anova(leafDC)
```

```{r}
leafTB <- lm(num.leaf ~ treatment, 
             data = combTB2[combTB2$treatment != "CON" & combTB2$dev.complete == "yes", ])

summary(leafTB)
anova(leafTB)
```

### Number of pods vs. herbivory and treatment group - NOT SIGNIFICANT

```{r}
podherbDC <- lm(num.pod.m ~ num.leaf, data = combDC2)

summary(podherbDC)
anova(podherbDC)
```


```{r}
podherbTB <- lm(num.pod.m ~ num.leaf, data = combTB2)

summary(podherbTB)
anova(podherbTB)
```

```{r}
podtrtDC <- lm(num.pod.m ~ treatment, data = combDC2)

summary(podtrtDC)
anova(podtrtDC)
```


```{r}
podtrtTB <- lm(num.pod.m ~ treatment, data = combTB2)

summary(podtrtTB)
anova(podtrtTB)
```

### Seed set vs. herbivory and treatment - NOT SIGNIFICANT

```{r}
reproDC <- lm(repro ~ num.leaf, data = combDC2)

summary(reproDC)
anova(reproDC)
```

```{r}
reproTB <- lm(repro ~ num.leaf, data = combTB2)

summary(reproTB)
anova(reproTB)
```

```{r}
reprotrtDC <- lm(repro ~ treatment, data = combDC2)

summary(reprotrtDC)
anova(reprotrtDC)
```

```{r}
reprotrtTB <- lm(repro ~ treatment, data = combTB2)

summary(reprotrtTB)
anova(reprotrtTB)
```

### Germination success vs. herbivory and treatment - NOT SIGNIFICANT

```{r}
germherbDC <-  glmer(prop.sprouted ~ num.leaf + (1|flat), data = combDCgerm, family = binomial, weights = num.seeds)

summary(germherbDC)
```

```{r}
germherbTB <-  glmer(prop.sprouted ~ num.leaf + (1|flat), data = combTBgerm, family = binomial, weights = num.seeds)

summary(germherbTB)
```



```{r}
germtrtDC <-  glmer(prop.sprouted ~ treatment + (1|flat), data = combDCgerm, family = binomial, weights = num.seeds)

summary(germtrtDC)
```


```{r}
germtrtTB <-  glmer(prop.sprouted ~ treatment + (1|flat), data = combTBgerm, family = binomial, weights = num.seeds)

summary(germtrtTB)
```

