---
title: "Prelimnary Data Analysis - TBDCFitness"
output: html_notebook
---

This notebook is to write preliminary code for data analysis for Tyler's 395 project related to the 2021 TBDCFitness experiment. 

## 0. Load Packages

```{r}
library(ggplot2)
library(lubridate)
library(lme4)
library(dplyr)
```

# PART I: Pod number 

## 1. Load in the data

```{r}
exit <- read.csv("~/Desktop/exitdatatest3.csv")
id <- read.csv("~/Desktop/IDtreatmenttest.csv")
```

## 2. Manipulate data
### a. Get treatment and type into exit data

```{r}
id <- id[, 1:3]
exit2 <- merge(exit, id, by.x = "PID", by.y = "pid")
```

### b. Get total number of pods

```{r}
exit2$num.pod.tot <- exit2$num.pod.m + exit2$num.pod.im
```

### c. Condition as a factor
```{r}
exit2$condition <- as.factor(exit2$condition)
```


## 3. Run stats

```{r}
mod1 <- lm(num.pod.tot ~ treatment*type, data = exit2)
anova(mod1)
```

```{r}
mod2 <- lm(num.pod.tot ~ condition*type, data = exit2)
anova(mod2)
```

## 4. Graph! 

### Number of pods vs. Treatment

```{r}
ggplot(data = exit2, aes(x = treatment, y = num.pod.tot)) + 
  theme_bw() + 
  geom_boxplot() + 
  ylim(0, 150) + 
  labs(x = "Treatment", y = "Total number of pods produced")
```
#### Broken up by plant type

```{r}
ggplot(data = exit2, aes(x = treatment, y = num.pod.tot)) + 
  theme_bw() + 
  geom_boxplot() + 
  labs(x = "Treatment", y = "Total number of pods produced") + 
  facet_wrap(~type)
```

#### Just mature pods

```{r}
ggplot(data = exit2, aes(x = treatment, y = num.pod.m)) + 
  theme_bw() + 
  geom_boxplot() + 
  labs(x = "Treatment", y = "Number of mature pods produced") + 
  facet_wrap(~type)
```
#### By condition

```{r}
ggplot(data = exit2, aes(x = condition, y = num.pod.tot)) + 
  theme_bw() + 
  geom_boxplot() + 
  labs(x = "Condition at time of exit", y = "Total number of pods produced") + 
  facet_wrap(~type) + 
  ylim(0,150)
```

# PART II: Herbivory

## 1. Load in the data

```{r}
herb <- read.csv("~/Desktop/herbivorytest.csv")
```

## 2. Write a for loop to get out total # of leaves eaten off of each plant. 

### a. Create a list of plant IDs

```{r}
ids <- id[, 1]
```

### b. Create the output file

```{r}
output <- id
output$leaves.eaten <- NA
```

### c. Remove rows in num.leaf that say "GONE", etc. 

```{r}
herb <- herb[herb$position !="", ]

```


### d. Write the for loop 

```{r}
for(i in 1:length(ids)){
  id.temp = ids[[i]]
  df.temp = herb[herb$pid == id.temp, ]
  output.temp = max(df.temp$num.leaf)
  output[i, 4] <- output.temp
}
```

## 3. Combine with pod data

```{r}
exitslim <- exit2[, c(1, 4, 11:13)]
comb <- merge(exitslim, output, by.x = c("PID", "treatment", "type"), by.y = c("pid", "treatment", "type"))
comb$leaves.eaten <- as.numeric(comb$leaves.eaten)
```

## 4. Graph!! 

### Pod number vs. leaf number

```{r}
ggplot(data = comb, aes(x = leaves.eaten, y = num.pod.tot, color = treatment)) + 
  theme_bw() + 
  geom_point() + 
  geom_smooth(method = "lm") + 
  labs(x = "Number of leaves consumed", y = "Total number of pods produced") + 
  facet_wrap(~type)
```


```{r}

```

