---
title: "Calculating total reproductive output"
output: html_notebook
---

This notebook will create our total reproductive output metric, and graph it against herbivory. 


## 0. Load libraries and data

```{r}
library(tidyverse)
library(ggplot2)
#library(lme4)
library(lmerTest)
```

```{r}
herb <- read.csv("~/Desktop/GitHub/TBDCFit/Data/HerbivoryCleaned.csv", header = TRUE)
germ <- read.csv("~/Desktop/GitHub/TBDCFit/Data/GermCollated.csv", header = TRUE)
key <- read.csv("~/Desktop/GitHub/TBDCFit/Data/pidTrtKey.csv", header = TRUE)
pods <- read.csv("~/Desktop/GitHub/TBDCFit/Data/ExitData.csv", header = TRUE)
TBseed <- read.csv("~/Desktop/GitHub/TBDCFit/Data/TBSeed.csv", header = TRUE)
DCseed <- read.csv("~/Desktop/GitHub/TBDCFit/Data/DCSeed.csv", header = TRUE)
```

## 1. Clean the data

Keep necessary columns

```{r}
herb <- herb %>%
  select(pid, type, num.leaf)

germ <- germ %>%
  select(pid, flat, num.seeds, prop.sprouted)

key <- key %>%
  select(pid, treatment, column)
```

Combine datasets

```{r}
comb <- merge(herb, germ, by = "pid")
comb <- merge(comb, key, by = "pid")
```

### Convert num leaf to area

```{r}
combDC <- comb[comb$type == "DC", ]
combTB <- comb[comb$type == "TB", ]

combDC$area.leaf <- combDC$num.leaf * (((104.55 + 105.84 + 91.82)/3))
combTB$area.leaf <- combTB$num.leaf * (1.5*((143.17 + 212.06 + 152.22)/3))

comb <- rbind(combDC, combTB)
comb$area.leaf <- comb$area.leaf / 10000

#comb$ln.area.leaf <- log(comb$area.leaf + 1)
 

```

### Get seed set per plant


Remove the individuals that had mature pods that we couldn't measure due to damage/mold

```{r}
TBseed <- TBseed[TBseed$pid != 23, ]
TBseed <- TBseed[TBseed$pid != 141, ]
```

```{r}
pods <- pods[pods$PID != 23, ]
pods <- pods[pods$PID != 141, ]
```

Remove unneeded rows from TBseed and pods

```{r}
TBseed <- TBseed %>%
  select(pid, mature, kept, pod.avg, holes.)
```

```{r}
pods <- pods %>%
  select(PID, num.pod.m)
```

### Write a for loop to get avg seed number per pod for DC

```{r}
#1. List of unique PIDs in DCseed

DCpid <- unique(DCseed$pid)

#2. Make output dataset

DCseedout <- data.frame(pid = DCpid, 
                        pod.avg = 0)

#3. write the for loop 

for(i in 1:length(DCpid)){
  subset <- DCseed[DCseed$pid == DCpid[i], ]
  DCseedout[i, 2] <- mean(subset$num.m.seeds)
}
```

### Remove DC where we couldn't find pods / pods rotten

```{r}
DCseedout <- DCseedout[DCseedout$pid != 78, ]
DCseedout <- DCseedout[DCseedout$pid != 140, ]
```

### Remove pods with spodoptera damage

```{r}
TBseed <- TBseed[TBseed$holes. != "yes", ]
```

### Remove TB plants without mature seeds

```{r}
TBseed <- TBseed[complete.cases(TBseed[, 4]), ]
```

### Convert TB pod masses to seed masses

```{r}
TBseed$seed.avg <- TBseed$pod.avg - 82.9 ##average mass of seed pod husk from 5/30
TBseed <- TBseed[TBseed$seed.avg > 0,  ]

TBseed <- TBseed %>%
  select(pid, seed.avg)
```

## 2. Get standardized seed set metric

1. Multiply avg seed set per plant by number of mature pods produced
2. Get mean of control group seed set by each  plant type
3. Divide each individual by that mean 
4. Combine into one dataset 

### Step 1


```{r}
DCseedout <- merge(DCseedout, pods, by.x = "pid", by.y = "PID")
TBseed <- merge(TBseed, pods, by.x = "pid", by.y = "PID")

DCseedout$tot.seed.set <- DCseedout$pod.avg * DCseedout$num.pod.m
TBseed$tot.seed.set <- TBseed$seed.avg * TBseed$num.pod.m
```


```{r}
DCseedout <- merge(DCseedout, key, by = "pid")

DCseedout <- DCseedout %>%
  select(pid, treatment, tot.seed.set)

DCseedCON <- DCseedout[DCseedout$treatment == "CON", ]

medianDC <- median(DCseedCON$tot.seed.set)

```


```{r}
TBseed <- merge(TBseed, key, by = "pid")

TBseed <- TBseed %>%
  select(pid, treatment, tot.seed.set)

TBseedCON <- TBseed[TBseed$treatment == "CON", ]

medianTB <- median(TBseedCON$tot.seed.set)

```


### Step 2

```{r}
DCseedout$stand.seed <- DCseedout$tot.seed.set / medianDC

TBseed$stand.seed <- TBseed$tot.seed.set / medianTB
```



## 3. Combine everything together

```{r}
comb <- merge(comb, pods, by.x = "pid", by.y = "PID")

comb <- merge(comb, DCseedout, by = c("pid", "treatment"), all.x = TRUE)
comb <- merge(comb, TBseed, by = c("pid", "treatment"), all.x = TRUE)

comb$stand.seed.set <- paste(comb$stand.seed.x, comb$stand.seed.y, sep = "")
comb$stand.seed.set <- gsub("NA", "", comb$stand.seed.set)
```

Remove plants where they didn't have any seeds

```{r}
comb <- comb[comb$stand.seed.set > 0, ]
```

Remove plants that didn't germinate at all **ASK BECKY**

```{r}
comb <- comb[comb$prop.sprouted > 0, ]
```


### Calculate fitness: 

```{r}
comb$stand.seed.set <- as.numeric(comb$stand.seed.set)
comb$ln.stand.seed.set <- log(comb$stand.seed.set)

comb$rel.fitness <- comb$prop.sprouted * comb$ln.stand.seed.set
```


## 4. Run some models:

```{r}
modseedset <- lmer(ln.stand.seed.set ~ area.leaf*type + (1|column), data = comb)

summary(modseedset)

```

```{r}
modgerm <- glmer(prop.sprouted ~ area.leaf*type + (1|column), data = comb, family = "binomial", weights = num.seeds)

summary(modgerm)
```


```{r}
modfitness <- lmer(rel.fitness ~ area.leaf*type + (1|column), data = comb)

summary(modfitness)
```

```{r}
plot(modfitness)
```



## 5. Graph things

```{r}
seedsetplot <- ggplot(data = comb, aes(x = area.leaf, y = ln.stand.seed.set)) + 
  geom_smooth(aes(linetype = type), color = "black", method = "lm", alpha = 0.2) + 
  scale_linetype_manual(values = c("solid", "dotdash")) +
  geom_point(aes(shape = type,  color = treatment)) + 
  theme_bw() + 
  scale_color_manual(values = c("#1E88E5", "lime green", "orange", "#D81B60")) + 
  scale_shape_manual(values = c(16, 5)) + 
  labs(x = expression(paste("Leaf area consumed ", (m^{2}))), y = "Standardized seed set", 
       color = "Treatment group",shape = "Hostplant", linetype = "Hostplant")

seedsetplot

ggsave("~/Desktop/GitHub/TBDCFit/Figures/seedsetherb.png", seedsetplot, width = 8, height = 5)
```


```{r}
germplot <- ggplot(data = comb, aes(x = area.leaf, y = prop.sprouted, shape = type)) + 
  geom_smooth(aes(linetype = type), color = "black", method = "lm", alpha = 0.2) + 
  scale_linetype_manual(values = c("solid", "dotdash")) + 
  geom_point(aes(color = treatment)) + 
  theme_bw() + 
  ylim(0, 1) + 
  scale_color_manual(values = c("#1E88E5", "lime green", "orange", "#D81B60")) + 
  scale_shape_manual(values = c(16, 5)) + 
  labs(x = expression(paste("Leaf area consumed ", (m^{2}))), y = "Proportion of seeds sprouted", 
       color = "Treatment group", shape = "Hostplant", linetype = "Hostplant") 

germplot
ggsave("~/Desktop/GitHub/TBDCFit/Figures/germherb.png", germplot, width = 8, height = 5)
  
```



```{r}
fitnessplot <- ggplot(data = comb, aes(x = area.leaf, y = rel.fitness)) + 
  geom_smooth(aes(linetype = type), color = "black", method = "lm", alpha = 0.2) + 
  scale_linetype_manual(values = c("solid", "dotdash")) + 
  geom_point(aes(shape = type,  color = treatment)) + 
  theme_bw() + 
  scale_color_manual(values = c("#1E88E5", "lime green", "orange", "#D81B60")) + 
  scale_shape_manual(values = c(16, 5)) + 
  labs(x = expression(paste("Leaf area consumed ", (m^{2}))), y = "Relative fitness", color = "Treatment group",
       shape = "Hostplant", linetype = "Hostplant")

fitnessplot

ggsave("~/Desktop/GitHub/TBDCFit/Figures/fitnessherb.png", fitnessplot, width = 8, height = 5)

```

```{r}
cormodel <- lm(ln.stand.seed.set ~ prop.sprouted, data = comb)
summary(cormodel)


ggplot(aes(x = prop.sprouted, y = ln.stand.seed.set), data = comb) + 
  geom_point(aes(color = type)) + 
  geom_smooth(method = "lm")
```


